---
title: "Figure 5. Observed vs. predicted activity levels"
author: "Michael Kearney"
date: "`r Sys.Date()`"
output: pdf_document
classoption: landscape
vignette: >
  %\VignetteIndexEntry{Figure 1. Observed vs. predicted body temperatures}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
 eval = TRUE, tidy.opts = list(width.cutoff = 60), tidy = TRUE  
)
```

## Overview

This document reads in the output produced by the file "Tiliqua rugosa simulation at Bundey Bore.Rmd" and the observed activity (waddle) data and compares them for each lizard in 2009 and 2010. It saves the summary statistics (correlation coefficient, root mean square error and confusion matrix) to files in the folder 'waddle test'. 

## Set up simulation and load the input data

```{r}
# First load the necessary packages and functions

library(NicheMapR)
library(raster)
library(dismo)
library(knitr)
library(mda)
source('addTrans.R') # function for making transparent plots

correl_all_2009 <- read.csv('correl_all_2009.csv')[,-1]
correl_all_2010 <- read.csv('correl_all_2010.csv')[,-1]
allforage_2009 <- read.csv('allforage_2009.csv')[,-1]
allforage_2010 <- read.csv('allforage_2010.csv')[,-1]
allnoforage_2009 <- read.csv('allnoforage_2009.csv')[,-1]
allnoforage_2010 <- read.csv('allnoforage_2010.csv')[,-1]

# Read in ectotherm model simulation

load('ecto.Rda')

ystart <- 1991# start year
yfinish <- 2010# end year
nyears<-yfinish - ystart+1# integer, number of years for which to run the microclimate model

# extract ectotherm model output
metout <- as.data.frame(ecto$metout)
rainfall <- as.data.frame(ecto$RAINFALL)
foodwaters <- as.data.frame(ecto$foodwaters)
foodlevels <- as.data.frame(ecto$foodlevels)
environ <- as.data.frame(ecto$environ)
debout <- as.data.frame(ecto$debout)
foodwaters <- as.data.frame(ecto$foodwaters)
foodlevels <- as.data.frame(ecto$foodlevels)
environ<-cbind(environ, metout$SOLR) # add solar radiation
colnames(environ)[ncol(environ)] <- "Solar"

# append dates
tzone <- paste("Etc/GMT-",10, sep = "") # doing it this way ignores daylight savings!
dates <- seq(ISOdate(ystart, 1, 1, tz = tzone)-3600*12, ISOdate((ystart+nyears),1, 1, tz = tzone)-3600*13, by = "hours")
dates <- subset(dates, format(dates, "%m/%d")!= "02/29") # remove leap years
dates2 <- seq(ISOdate(ystart, 1, 1, tz = tzone)-3600*12, ISOdate((ystart+nyears),1, 1, tz = tzone)-3600*13, by = "days") 
dates2 <- subset(dates2, format(dates2, "%m/%d")!= "02/29") # remove leap years

debout <- as.data.frame(cbind(dates, debout))
environ <- as.data.frame(cbind(dates, environ))
metout <- as.data.frame(cbind(dates, metout))
rainfall <- as.data.frame(cbind(dates2, rainfall))
colnames(rainfall) <- c("dates", "rainfall")
```

## Read in Mike Bull's data and merge with predictions

```{r}
waddlefiles <- read.csv("waddleometer/waddle_files_all.csv")
massdata <- read.csv('waddleometer/Church_site_mass_length_noJan2010.csv')
sex <- read.csv("waddleometer/sex.csv",stringsAsFactors = FALSE)

#Subset to 2009-2010 and frame-shift by half an hour to account for 1/2 hr time difference in South Australia

merge <- as.data.frame(paste(with(environ, as.numeric(format(dates, "%Y"))),"_",with(environ, as.numeric(format(dates, "%m"))),"_",with(environ, as.numeric(format(dates, "%d"))),"_",environ$TIME-1, sep = ""))
colnames(merge) <- 'merge'
environ2 <- cbind(environ, merge)
environ3 <- environ2
environ4 <- subset(environ3, format(dates,"%Y")>=2009)
environ5 <- environ4
for(l in 1:nrow(environ4)){ # make values average of prev hour to account for 1/2 time diff in SA
  if(l==nrow(environ4)){
    environ5[l, 6] <- environ4[l, 6]
  }else{
    environ5[l, 6] <- environ5[l, 6]+(environ4[l+1, 6]-environ4[l, 6])/2
  }
}
```

## Figure 5 Movement rate vs Tb

```{r}
TBASK <- 26
threshold.act <- 50
startdy <- 250
finishdy <- 355

allforage <- allforage_2010
allnoforage <- allnoforage_2010

# find times when lizards were moving and not moving
allforage <- subset(allforage,  subset = (Steps > threshold.act))
curyear <- 2010

filename=paste("Figure 5.pdf",sep="") 
pdf(filename,paper="A4",width=11,height=15) 

par(mfrow = c(3, 1)) # set up for 2 plots in 2 columns
par(oma = c(2, 2, 2, 2) + 0.1) # margin spacing
par(mar = c(5, 5, 2, 1) + 0.1) # margin spacing 
par(mgp = c(3, 1, 0) ) # margin spacing

# Plot part a, mean activity of all animals

sleepy_id <- 11885
sleepy <- as.data.frame(read.table(file = paste('waddle/', sleepy_id, '_2010_ALL.csv' ,sep = ""), sep = ",", head=TRUE))
date_waddle1 <- with(sleepy, ISOdatetime(Year, Month, Day, Hours, Minutes, 0)) # create date
date_waddle <- date_waddle1 + 60*60 # adjust for Central Time
doy <- strptime(format(date_waddle, "%y/%m/%d"), "%y/%m/%d")$yday + 1 # get waddle day of year
plotrainfall <- subset(rainfall,substr(dates,1,4)==curyear)
doy2 <- strptime(format(plotrainfall$dates, "%y/%m/%d"), "%y/%m/%d")$yday + 1 # get simulation day of year
sleepy <- cbind(date_waddle, doy, sleepy) # append dates and day of year to sleepy data
      
environ_bask <- subset(environ5,  subset = (ACT >= 1 & TC >= TBASK & substr(dates, 1, 4) == curyear))
environ_forage <- subset(environ5,  subset = (ACT > 1 & substr(dates, 1, 4) == curyear))
environ_night <- subset(metout,  subset = (ZEN == 90))
environ_night$TIME <- environ_night$TIME/60-1

agglist <- list(paste(sleepy$Year, "_", sleepy$Month, "_", sleepy$Day, "_", sleepy$Hours, sep = ""))
date_waddle <- aggregate(sleepy$date_waddle, by = agglist, min)
doy <- aggregate(sleepy$doy, by = agglist,max)
Tb <- aggregate(sleepy$Temperature, by = agglist,mean)
steps <- aggregate(sleepy$Steps, by = agglist,sum)
year <- aggregate(sleepy$Year, by = agglist,max)
month <- aggregate(sleepy$Month, by = agglist,max)
day <- aggregate(sleepy$Day, by = agglist,max)
hours <- aggregate(sleepy$Hours, by = agglist,max)
sleepy <- as.data.frame(cbind(as.data.frame(date_waddle[,2]),doy[,2],Tb[,2],steps[,2],year[,2],month[,2],day[,2],hours[,2]))
colnames(sleepy) = c('date_waddle','doy','Temperature','Steps','Year','Month','Day','Hours')
doy2 <- strptime(format(plotrainfall$dates, "%y/%m/%d"), "%y/%m/%d")$yday+1
plotrainfall2 <- cbind(doy2, plotrainfall)
colnames(plotrainfall2) <- c("JULDAY", "dates", "RAINFALL")
desic <- subset(debout,TIME == 24 & substr(dates, 1, 4) == curyear)
desic <- as.data.frame(cbind(desic[,2], desic[,20]))
colnames(desic) <- c('day','desic')

# plot night hours
with(environ_night, {plot(TIME+2~JULDAY, xlim = c(startdy, finishdy), ylim = c(0, 25), xlab = "day of year", ylab = "hour of day", cex = 0.5, col = "dark grey", pch = 16, main = "a) mean observed activity vs. potential activity", cex.lab = 1.5, cex.main = 1.5)})

# plot basking hours      
with(environ_bask, {points(TIME~JULDAY, xlim = c(startdy, finishdy), ylim = c(0, 25),xlab = "day of year", ylab = "hour of day", cex = 1.,col = "light blue", pch = 15)})

# plot foraging hours
with(environ_forage, {points(TIME~JULDAY, xlim = c(startdy, finishdy), ylim = c(0, 25), xlab = "day of year", ylab = "hour of day", cex = 1., col = "light blue", pch = 15)})

with(plotrainfall2, {points(RAINFALL~JULDAY, type = "h",col='blue')})

agglist <- list(paste(allforage$Year, "_", allforage$Month, "_", allforage$Day, "_", allforage$Hours, sep=""))

# get mean steps per hour across all lizards and plot
meanwaddle <- aggregate(allforage$Steps, by = agglist, mean)
meanhour <- aggregate(allforage$Hours,by = agglist, mean)
meandoy <- aggregate(allforage$doy,by = agglist, mean)
meanwaddle <- cbind(meanwaddle,meanhour[,2], meandoy[,2])
colnames(meanwaddle) <- c('date', 'Steps', 'Hours', 'doy')
with(meanwaddle, {points(Hours + 1 ~ doy, xlim = c(startdy, finishdy), ylim = c(0, 25),xlab = "day of year",ylab = "hour of day", cex = log(meanwaddle$Steps/300), pch = 15, col = addTrans("red", 100))}) 

arrows(248, 16.5, 248, 14.5, lwd = 2, angle = 10, length = 0.1)
arrows(257, 17.5, 257, 15.5, lwd = 2, angle = 10, length = 0.1)
arrows(263, 17.5, 263, 15.5, lwd = 2, angle = 10, length = 0.1)
arrows(289, 16.5, 289, 14.5, lwd = 2, angle = 10, length = 0.1)
arrows(317, 25.5, 317, 23.5, lwd = 2, angle = 10, length = 0.1)
arrows(341, 4.5, 341, 2.5, lwd = 2, angle = 10, length = 0.1)

# Part b, high activity individual 11885 

# plot night hours
with(environ_night, {plot(TIME+2~JULDAY, xlim = c(startdy, finishdy), ylim = c(0, 25), xlab = "day of year", ylab = "hour of day", cex = 0.5, col = "dark grey", pch = 16, main = "b) male 11885 observed activity vs. potential activity", cex.lab = 1.5, cex.main = 1.5)})

# plot basking hours      
with(environ_bask, {points(TIME~JULDAY, xlim = c(startdy, finishdy), ylim = c(0, 25),xlab = "day of year", ylab = "hour of day", cex = 1.,col = "light blue", pch = 15, )})

# plot foraging hours
with(environ_forage, {points(TIME~JULDAY, xlim = c(startdy, finishdy), ylim = c(0, 25), xlab = "day of year", ylab = "hour of day", cex = 1., col = "light blue", pch = 15)})

with(plotrainfall2, {points(RAINFALL~JULDAY, type = "h",col='blue')})

# find times when lizards were moving and not moving
plotlizard_forage <- subset(sleepy,  subset = (Steps > threshold.act))

# plot observed foraging
with(plotlizard_forage, {points(Hours+1~doy, xlim = c(startdy, finishdy),ylim = c(0, 25),xlab = "day of year",ylab = "hour of day",cex = log(plotlizard_forage$Steps/300),pch = 15, col = addTrans("red",100))})

# Part c, low activity individual 11533

sleepy_id <- 11533
sleepy <- as.data.frame(read.table(file = paste('waddle/', sleepy_id, '_2010_ALL.csv', sep = ""), sep = ",", head=TRUE))
date_waddle1 <- with(sleepy, ISOdatetime(Year, Month, Day, Hours, Minutes, 0)) # create date
date_waddle <- date_waddle1 + 60*60 # adjust for Central Time
doy <- strptime(format(date_waddle, "%y/%m/%d"), "%y/%m/%d")$yday + 1 # get waddle day of year
doy2 <- strptime(format(plotrainfall$dates, "%y/%m/%d"), "%y/%m/%d")$yday + 1 # get simulation day of year
sleepy <- cbind(date_waddle, doy, sleepy) # append dates and day of year to sleepy data
      
agglist <- list(paste(sleepy$Year, "_", sleepy$Month, "_", sleepy$Day, "_", sleepy$Hours, sep = ""))
date_waddle <- aggregate(sleepy$date_waddle, by = agglist, min)
doy <- aggregate(sleepy$doy, by = agglist,max)
Tb <- aggregate(sleepy$Temperature, by = agglist,mean)
steps <- aggregate(sleepy$Steps, by = agglist,sum)
year <- aggregate(sleepy$Year, by = agglist,max)
month <- aggregate(sleepy$Month, by = agglist,max)
day <- aggregate(sleepy$Day, by = agglist,max)
hours <- aggregate(sleepy$Hours, by = agglist,max)
sleepy <- as.data.frame(cbind(as.data.frame(date_waddle[,2]),doy[,2],Tb[,2],steps[,2],year[,2],month[,2],day[,2],hours[,2]))
colnames(sleepy) = c('date_waddle','doy','Temperature','Steps','Year','Month','Day','Hours')

# plot night hours
with(environ_night, {plot(TIME+2~JULDAY, xlim = c(startdy, finishdy), ylim = c(0, 25), xlab = "day of year", ylab = "hour of day", cex = 0.5, col = "dark grey", pch = 16, main = "c) female 11533 observed activity vs. predicted feeding events", cex.lab = 1.5, cex.main = 1.5)})

# plot foraging hours
with(environ_forage, {points(TIME~JULDAY, xlim = c(startdy, finishdy), ylim = c(0, 25), xlab = "day of year", ylab = "hour of day", cex = 1., col = "light blue", pch = 15)})

with(plotrainfall2, {points(RAINFALL~JULDAY, type = "h",col='blue')})

# find times when lizards were moving and not moving
plotlizard_forage <- subset(sleepy,  subset = (Steps > threshold.act))

# plot observed foraging
with(plotlizard_forage, {points(Hours+1~doy, xlim = c(startdy, finishdy),ylim = c(0, 25),xlab = "day of year",ylab = "hour of day",cex = log(plotlizard_forage$Steps/300),pch = 15, col = addTrans("red",100))})

dev.off()
```