---
title: "Figure 4. Observed movement rate vs body temperature"
author: "Michael Kearney"
date: "`r Sys.Date()`"
output: pdf_document
classoption: landscape
vignette: >
  %\VignetteIndexEntry{Figure 1. Observed vs. predicted body temperatures}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
 eval = TRUE, tidy.opts = list(width.cutoff = 60), tidy = TRUE  
)
```

## Overview

This document reads in waddleometer data files for all 121 lizards and computes speed from step frequency using the formulae in Kerr et al. 2004. It then plots the relationship between movement speed and body temperature. It also estimates the rate as a function of the Arrhenius temprature response used for the Dynamic Energy Budget model.

## Collate data

```{r, eval = FALSE}
waddlefiles<-read.csv("waddleometer//waddle_files_all.csv")
sex<-read.csv("waddle/sex.csv", stringsAsFactors = FALSE)

for(i in 1:121){
    sleepy_id <- waddlefiles[i, 2] # get lizard ID
    sexlizard <- as.character(subset(sex, Liz==sleepy_id)[2]) # get lizard sex
    if(sexlizard == "u" | sexlizard == "character(0)"){
      sexlizard <- 'unknown'
    }

    sleepy <- as.data.frame(read.table(file = paste('waddle/',waddlefiles[i, 3],sep = ""), sep = ",", head = TRUE, stringsAsFactors = FALSE)) # read in data

    if(i == 1){
     speedTemp <- cbind(sleepy_id, sexlizard, as.data.frame(cbind(sleepy$Year, sleepy$Month, sleepy$Day, sleepy$Hours, sleepy$Minutes, sleepy$Temperature, sleepy$Steps),stringsAsFactors = FALSE))
    #with(sleepy,plot(speed ~ Temperature, type='p', cex= 0.3, ylim = c(0,3), xlim=c(0, 50), ylab = "Speed (km / h)", xlab=expression(paste("Body Temperature (",degree,"C)"))))
    }else{
    #  with(sleepy, points(speed ~ Temperature, type = 'p', cex = 0.3))
      speedTemp <- rbind(cbind(sleepy_id, sexlizard, as.data.frame(cbind(sleepy$Year, sleepy$Month, sleepy$Day, sleepy$Hours, sleepy$Minutes, sleepy$Temperature, sleepy$Steps),stringsAsFactors = FALSE))) 
    }
cat(i, ' \n')
} #end loop through lizards
colnames(speedTemp) <- c("id", "sex", "year", "month", "day", "hour", "minute", "temperature", "steps")
save(speedTemp, file = "speedTemp.Rda")
```

## Compute observed and predicted speed

```{r}
load('speedTemp.Rda')

# Observed speed
RSL <- 0.0102 * speedTemp$steps / 2 + 2.282 # relative stride length (mm)
HLL <- 60 # hind limb length, mm for a 290 mm individual measured by Dale Burzacott on 4/8/2015
speedTemp$speed <- (RSL * HLL * (speedTemp$steps)) / 1000 / 1000 * 60 # sleepy speed in km / h - using formula in Kerr et al 2004 for distance as a function of relative stride length, stride frequency and hind limb length

# predicted speed

Tb20 <- subset(speedTemp, temperature == 20 & speed > 0)$speed
Tb20_speed <- mean(Tb20)

debpars <- as.data.frame(read.csv('DEB model/DEB_pars_Tiliqua_rugosa.csv',header = FALSE))$V1 # read in DEB pars
# set thermal respose curve paramters
T_REF <- debpars[1] - 273
TA <- debpars[2] # Arrhenius temperature (K)
TAL <- debpars[5] # low Arrhenius temperature (K)
TAH <- debpars[6] # high Arrhenius temperature (K)
TL <- debpars[3] # low temp boundary (K)
TH <- debpars[4] # hight temp boundary (K)
speedTemp$T_corr <- exp(TA*(1/(273.15+T_REF)-1/(273.15+speedTemp$temperature)))/(1+exp(TAL*(1/(273.15+speedTemp$temperature)-1/TL))+exp(TAH*(1/TH-1/(273.15+speedTemp$temperature)))) # correction from 20 to 33.5

speedTemp$pred <- Tb20_speed * speedTemp$T_corr

# Aggregate mean speed per temperature category

speedTemp_move <- subset(speedTemp, speed > 0) # remove non-moving lizards

agg_speedTemp_move <- aggregate(speedTemp_move, by = list(round(speedTemp_move$temperature)), FUN = mean)
```

## Plot results

```{r}
source("addTrans.R")

filename=paste("Figure 4.pdf",sep="") 
pdf(filename,paper="A4",width=9,height=5)

par(mfrow = c(1, 2)) # set up for 2 plots in 2 columns
par(oma = c(2, 2, 2, 2) + 0.1) # margin spacing stuff
par(mar = c(5, 5, 2, 1) + 0.1) # margin spacing stuff 
par(mgp = c(3, 1, 0) ) # margin spacing stuff

with(speedTemp,plot(speed ~ temperature, type='p', cex= 1, ylim = c(0,1.6), xlim=c(5, 42), col = addTrans("black", 20), pch = 16, ylab = "Speed (km / h)", xlab=expression(paste("Body Temperature (",degree,"C)"))))

#points(speedTemp$temperature, speedTemp$T_corr * Tb20_speed, type = 'p', pch = 16, col = 'red')

with(agg_speedTemp_move,plot(speed ~ temperature, type='p', cex= 1, xaxs = 'i', ylim = c(0,0.3), xlim=c(7, 40), col = "black", pch = 16, ylab = "Speed (km / h)", xlab=expression(paste("Body Temperature (",degree,"C)"))))

points(agg_speedTemp_move$temperature, agg_speedTemp_move$T_corr * Tb20_speed, type = 'p', pch = 16, col = 'red')

dev.off()
```

## Literature Cited

Kerr, G. D., C. M. Bull, and G. R. Cottrell. 2004. Use of an "on board" datalogger to determine lizard activity patterns, body temperature and microhabitat use for extended periods in the field. Wildlife Research 31:171-176.