---
title: "Figure 3. Observed vs. predicted body temperatures"
author: "Michael Kearney"
date: "`r Sys.Date()`"
output: pdf_document
classoption: landscape
vignette: >
  %\VignetteIndexEntry{Figure 1. Observed vs. predicted body temperatures}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
 eval = TRUE, tidy.opts = list(width.cutoff = 60), tidy = TRUE  
)
```

## Overview

This document reads in the output produced by the file "Tiliqua rugosa simulation at Bundey Bore.Rmd" and the observed $T_b$ dataand compares them for each lizard in 2009 and 2010. It saves the summary statistics (correlation coefficient, root mean square error and confusion matrix) to files in the folder 'waddle test'. 

## Set up simulation and load the input data

```{r}
# First load the necessary packages and functions

library(NicheMapR)
library(raster)
library(dismo)
library(knitr)
library(mda)
source('addTrans.R') # function for making transparent plots

correl_all_2009 <- read.csv('correl_all_2009.csv')[,-1]
correl_all_2010 <- read.csv('correl_all_2010.csv')[,-1]
allforage_2009 <- read.csv('allforage_2009.csv')[,-1]
allforage_2010 <- read.csv('allforage_2010.csv')[,-1]
allnoforage_2009 <- read.csv('allnoforage_2009.csv')[,-1]
allnoforage_2010 <- read.csv('allnoforage_2010.csv')[,-1]

# Read in ectotherm model simulation

load('ecto.Rda')

ystart <- 1991# start year
yfinish <- 2010# end year
nyears<-yfinish - ystart+1# integer, number of years for which to run the microclimate model

# extract ectotherm model output
metout <- as.data.frame(ecto$metout)
rainfall <- as.data.frame(ecto$RAINFALL)
foodwaters <- as.data.frame(ecto$foodwaters)
foodlevels <- as.data.frame(ecto$foodlevels)
environ <- as.data.frame(ecto$environ)
debout <- as.data.frame(ecto$debout)
foodwaters <- as.data.frame(ecto$foodwaters)
foodlevels <- as.data.frame(ecto$foodlevels)
environ<-cbind(environ, metout$SOLR) # add solar radiation
colnames(environ)[ncol(environ)] <- "Solar"

# append dates
tzone <- paste("Etc/GMT-",10, sep = "") # doing it this way ignores daylight savings!
dates <- seq(ISOdate(ystart, 1, 1, tz = tzone)-3600*12, ISOdate((ystart+nyears),1, 1, tz = tzone)-3600*13, by = "hours")
dates <- subset(dates, format(dates, "%m/%d")!= "02/29") # remove leap years
dates2 <- seq(ISOdate(ystart, 1, 1, tz = tzone)-3600*12, ISOdate((ystart+nyears),1, 1, tz = tzone)-3600*13, by = "days") 
dates2 <- subset(dates2, format(dates2, "%m/%d")!= "02/29") # remove leap years

debout <- as.data.frame(cbind(dates, debout))
environ <- as.data.frame(cbind(dates, environ))
metout <- as.data.frame(cbind(dates, metout))
rainfall <- as.data.frame(cbind(dates2, rainfall))
colnames(rainfall) <- c("dates", "rainfall")
```

## Read in Mike Bull's data and merge with predictions

```{r}
waddlefiles <- read.csv("waddleometer/waddle_files_all.csv")
massdata <- read.csv('waddleometer/Church_site_mass_length_noJan2010.csv')
sex <- read.csv("waddleometer/sex.csv",stringsAsFactors = FALSE)

#Subset to 2009-2010 and frame-shift by half an hour to account for 1/2 hr time difference in South Australia

merge <- as.data.frame(paste(with(environ, as.numeric(format(dates, "%Y"))),"_",with(environ, as.numeric(format(dates, "%m"))),"_",with(environ, as.numeric(format(dates, "%d"))),"_",environ$TIME-1, sep = ""))
colnames(merge) <- 'merge'
environ2 <- cbind(environ, merge)
environ3 <- environ2
environ4 <- subset(environ3, format(dates,"%Y")>=2009)
environ5 <- environ4
for(l in 1:nrow(environ4)){ # make values average of prev hour to account for 1/2 time diff in SA
  if(l==nrow(environ4)){
    environ5[l, 6] <- environ4[l, 6]
  }else{
    environ5[l, 6] <- environ5[l, 6]+(environ4[l+1, 6]-environ4[l, 6])/2
  }
}
```

## Figure 3 Predicted and observed Tb

```{r}
TBASK <- 26 # min Tb at which leaves retreat, from Pamula (1997) Table 3.14

filename=paste("Figure 3.pdf",sep="") 
pdf(filename,paper="A4r",width=15,height=11) 

par(mfrow = c(2, 2)) # set up for 2 plots in 2 columns
par(oma = c(2, 2, 2, 2) + 0.1) # margin spacing
par(mar = c(5, 5, 2, 1) + 0.1) # margin spacing 
par(mgp = c(3, 1, 0) ) # margin spacing

yearstodo=c(2009,2010)
for(m in 1:2){
  yeartodo=yearstodo[m]
  k=0
  
  plotrainfall <- subset(rainfall, substr(dates, 1, 4) == yeartodo) # get rainfall
  environ_bask <- subset(environ5,  subset = (ACT >= 1 & TC >= TBASK & substr(dates, 1, 4) == yeartodo)) # get basking hrs
  environ_forage <- subset(environ5,  subset = (ACT > 1 & substr(dates, 1, 4) == yeartodo))  # get foraging hrs
  environ_night <- subset(metout,  subset = (ZEN == 90)) # get night hours
  environ_night$TIME <- environ_night$TIME / 60 - 1 # convert from mins to hr
  
  for(i in 1:121){
    
    sleepy_id <- waddlefiles[i, 2] # get lizard ID
    sexlizard <- as.character(subset(sex, Liz==sleepy_id)[2]) # get lizard sex
    if(sexlizard == "u" | sexlizard == "character(0)"){
      sexlizard <- 'unknown'
    }
    if(sexlizard == 2){
      sexlizard <- 'F'
    }
    if(sexlizard == 3){
      sexlizard <- 'M'
    }
    
    sleepy <- as.data.frame(read.table(file = paste('waddle/',waddlefiles[i, 3],sep = ""), sep = ",", head = TRUE, stringsAsFactors = FALSE)) # read in data
    
    curyear=max(sleepy$Year,na.rm=TRUE)
    if(curyear==yeartodo){
      date_waddle1 <- with(sleepy, ISOdatetime(Year, Month, Day, Hours, Minutes, 0)) # create date
      date_waddle <- date_waddle1 + 60*60 # adjust for Central Time
      doy <- strptime(format(date_waddle, "%y/%m/%d"), "%y/%m/%d")$yday + 1 # get waddle day of year
      doy2 <- strptime(format(plotrainfall$dates, "%y/%m/%d"), "%y/%m/%d")$yday + 1 # get simulation day of year
      sleepy <- cbind(date_waddle, doy, sleepy) # append dates and day of year to sleepy data
      plotrainfall2 <- cbind(doy2, plotrainfall) # append day of year to rainfall data
      colnames(plotrainfall2) <- c("JULDAY", "dates", "RAINFALL")
      # create body condition vector      
      desic <- subset(debout, TIME == 24 & substr(dates, 1, 4) == curyear) 
      desic <- as.data.frame(cbind(desic[,2], desic[,20]))
      colnames(desic) <- c('day', 'desic')
      
      # aggregate sleepy lizard data by hour
      agglist <- list(paste(sleepy$Year, "_", sleepy$Month, "_", sleepy$Day, "_", sleepy$Hours, sep = ""))
      date_waddle <- aggregate(sleepy$date_waddle, by = agglist, min)
      doy <- aggregate(sleepy$doy, by = agglist,max)
      Tb <- aggregate(sleepy$Temperature, by = agglist,mean)
      steps <- aggregate(sleepy$Steps, by = agglist,sum)
      year <- aggregate(sleepy$Year, by = agglist,max)
      month <- aggregate(sleepy$Month, by = agglist,max)
      day <- aggregate(sleepy$Day, by = agglist,max)
      hours <- aggregate(sleepy$Hours, by = agglist,max)
      sleepy <- as.data.frame(cbind(as.data.frame(date_waddle[,2]),doy[,2],Tb[,2],steps[,2],year[,2],month[,2],day[,2],hours[,2]))
      colnames(sleepy) = c('date_waddle','doy','Temperature','Steps','Year','Month','Day','Hours')
      
      # round the times to get rid of occasional 1 min add-ons
      x <- sleepy$date_waddle
      r <-  60 * 60
      H <- as.integer(format(x, "%H"))
      M <- as.integer(format(x, "%M"))
      S <- as.integer(format(x, "%S"))
      D <- format(x, "%Y-%m-%d")
      secs <- 3600 * H + 60 * M + S
      x <- as.POSIXct(round(secs / r) * r, origin = D) - 11 * 3600
      sleepy$date_waddle <- x
      
      sleepy3=subset(sleepy,sleepy$Month<11)
      if(k==0){
        if(curyear==2009){
          with(sleepy3,plot(Temperature~date_waddle,col='red',cex=0.2,ylim=c(0,45),xlim=c(as.numeric(as.POSIXct("2009-09-15",origin="1970-01-01")),as.numeric(as.POSIXct("2009-10-15",origin="1970-01-01"))),ylab=expression(paste("Body Temperature (",degree,"C)")),xaxt = "n",xlab="", main = "a) observed and predicted body temperature vs. time, 2009"))
        }else{
          with(sleepy3,plot(Temperature~date_waddle,col='red',cex=0.2,ylim=c(0,45),xlim=c(as.numeric(as.POSIXct("2010-09-15",origin="1970-01-01")),as.numeric(as.POSIXct("2010-10-15",origin="1970-01-01"))),ylab=expression(paste("Body Temperature (",degree,"C)")),xaxt = "n",xlab="", main = "c) observed and predicted body temperature vs. time, 2010"))
        }
      }else{
        with(sleepy3,points(Temperature~date_waddle,col='red',cex=0.2,ylim=c(0,50)))
      }
      
      k=k+1
    }
  } #end loop through lizards
  k=0
  #points(metout$TAREF~environ$dates,cex=0.2,pch=16,col='grey',type='l',lty=2)
  points(environ5$TC~environ5$dates,cex=0.5,pch=16,type='b')
  axis.POSIXct(side = 1, x = environ5$dates,
    at = seq(from = round(environ5$dates[1], "days"),
      to = environ5$dates[1] + ceiling(difftime(tail(environ5$dates, 1), head(environ5$dates, 1), 
        units = "days")),
      by = "1 day"),
    las = 2)
  
  if(curyear == 2009){
    with(correl_all_2009,plot(Tb_pred~Tb_obs,col=addTrans("black",10),pch=16,cex=0.5,ylim=c(5,45),xlim=c(5,45), main = "b) observed vs. predicted body temperature, 2009",xlab=expression(paste("Observed Temperature (",degree,"C)")),ylab=expression(paste("Predicted Temperature (",degree,"C)"))))
    abline(0,1,col='black')
  }else{
    with(correl_all_2010,plot(Tb_pred~Tb_obs,col=addTrans("black",10),pch=16,cex=0.5,ylim=c(5,45),xlim=c(5,45), main = "b) observed vs. predicted body temperature, 2010",xlab=expression(paste("Observed Temperature (",degree,"C)")),ylab=expression(paste("Predicted Temperature (",degree,"C)"))))
    abline(0,1,col='black')
  }
}

dev.off()
```
