---
title: "Create Figure 9 hydration levels from Kerr & Bull 2004"
author: "Michael Kearney"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{Create Figure 9 hydration levels from Kerr & Bull 2004}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
 eval = TRUE, tidy.opts=list(width.cutoff=60), tidy=TRUE  
)
```

## Overview

This study takes the results of the 'Tiliqua rugosa simulation at Bundey Bore.Rmd' simulation and subsets it for the 2002/2003 summer when Greg Kerr studied body condition changes at Bundey Bore during a drought period. The predicted non-reproductive body mass, accounting for dehydration, is predicted and compared to observed values. The correlation between observed and predicted body mass is also determined.

## Extract results from ectotherm simulation and append dates

```{r}
load('ecto_nodepress.Rda')
ecto_nodepress <- ecto
load('ecto.Rda')
rainfall <- as.data.frame(ecto$RAINFALL)
debout <- as.data.frame(ecto$debout)
debout_nodepress <- as.data.frame(ecto_nodepress$debout)
foodwaters <- as.data.frame(ecto$foodwaters)
foodlevels <- as.data.frame(ecto$foodlevels)

# append dates
ystart <- 1991 # start year
yfinish <- 2010 # end year
nyears <- yfinish - ystart + 1# integer, number of years for which to run the microclimate model
tzone <- paste("Etc/GMT+", 10, sep="") 
dates <- seq(ISOdate(ystart, 1, 1, tz = tzone) - 3600 * 12, ISOdate((ystart+nyears), 1, 1, tz=tzone) - 3600 * 13, by="hours")
dates <- subset(dates, format(dates, "%m/%d")!= "02/29") # remove leap years
dates2 <- seq(ISOdate(ystart,1,1,tz=tzone)-3600*12, ISOdate((ystart+nyears), 1, 1, tz = tzone) - 3600 * 13, by = "days") 
dates2 <- subset(dates2, format(dates2, "%m/%d") != "02/29") # remove leap yearsdates=subset(dates, format(dates, "%m/%d")!= "02/29") # remove leap years

debout <- as.data.frame(cbind(dates, debout))
debout_nodepress <- as.data.frame(cbind(dates, debout_nodepress))
rainfall <- as.data.frame(cbind(dates2, rainfall))
colnames(rainfall) <- c("dates", "rainfall")
```

## Subset 2002/2003 data, compute non-reproductive, hydration-specific body mass

```{r}
plotdebout <- subset(debout, format(debout$dates, "%y") == "02" | format(debout$dates, "%y") == "03")
plotdebout_nodepress <- subset(debout_nodepress, format(debout_nodepress$dates, "%y") == "02" | format(debout_nodepress$dates, "%y") == "03")
plotfoodwaters <- subset(cbind(dates2, foodwaters),format(dates2, "%y") =="02" | format(dates2, "%y") == "03")
plotfoodlevels <- subset(cbind(dates2, foodlevels),format(dates2, "%y") =="02" | format(dates2, "%y") == "03")
# plot predicted body mass, excluding reproductive mass and subtracting away any mass lost as evaporation
mu_E <- 585000 # molar Gibbs energy (chemical potential) of reserve (J/mol)
hydration_mass_male <- plotdebout$WETMASS - (plotdebout$CUMREPRO + plotdebout$CUMBATCH) / mu_E * 23.9 / 0.3 - plotdebout$WETMASS * (plotdebout$Body_cond / 100)
hydration_mass_female <- plotdebout$WETMASS - plotdebout$WETMASS * (plotdebout$Body_cond / 100)
hydration_mass <- (hydration_mass_male + hydration_mass_female) / 2
hydration_mass_male_nodepress <- plotdebout_nodepress$WETMASS - (plotdebout_nodepress$CUMREPRO + plotdebout_nodepress$CUMBATCH) / mu_E * 23.9 / 0.3 - plotdebout_nodepress$WETMASS * (plotdebout_nodepress$Body_cond / 100)
hydration_mass_female_nodepress <- plotdebout_nodepress$WETMASS - plotdebout_nodepress$WETMASS * (plotdebout_nodepress$Body_cond / 100)
hydration_mass_nodepress <- (hydration_mass_male_nodepress + hydration_mass_female_nodepress) / 2
```

## Plot observed and predicted trajectory of body mass with rainfall and plant water levels

```{r}
# read in Kerr & Bull 2004 Figure 5 body mass data.
Kerr_fig5 <- read.csv("Kerr_Fig5.csv")
date_Kerr <- with(Kerr_fig5, ISOdatetime(Year, Month, Day, 0, 0, 0))
Kerr_fig5 <- cbind(date_Kerr, Kerr_fig5)

filename=paste("Figure 9.pdf",sep="") 
pdf(filename,paper="A4",width=11,height=5)
par(mfrow = c(1, 1)) # set up for 4 plots in 1 columns
par(oma = c(2, 2, 2, 2) + 0.1) # margin spacing
par(mar = c(5, 5, 2, 1) + 0.1) # margin spacing 
par(mgp = c(3, 1, 0) ) # margin spacing

plot(hydration_mass ~ plotdebout$dates, type = 'l', ylim = c(200, 800), ylab = "mass, g / rainfall / plant water", xlab = "", cex.axis = 1.2, cex.lab = 1.2, yaxs = 'i')
points(hydration_mass_nodepress ~ plotdebout_nodepress$dates, type = 'l', cex.axis = 1.2, cex.lab = 1.2, yaxs = 'i', col = 'grey')
with(Kerr_fig5, points(Mass ~ date_Kerr, type='p', col='red', pch = 16, cex = 1.2))
points((plotfoodwaters$`ecto$foodwaters`*200+200) ~ plotfoodwaters$dates2, type = 'h', col = 'dark green', lwd = 2)
points((rainfall$rainfall * 6 + 200) ~ rainfall$dates, type = 'h', col = 'light blue')
dev.off()
```

## Correlate observed and predicted body mass

```{r}
# aggregate hourly to daily body mass and append to Kerr2004 data
dailymass <- aggregate(hydration_mass, by = list(format(plotdebout$dates, "%Y-%m-%d")), FUN = mean)
Kerr_fig5 <- cbind(Kerr_fig5, dailymass[which(dailymass$Group.1 %in% as.character(Kerr_fig5$date_Kerr)),2])
colnames(Kerr_fig5)[8] <- "predMass"

# plot
x <- 300:800
plot(x,x, type = 'l', main='body condition',ylab = "observed mass, g", xlab = "predicted mass, g", ylim = c(450,600), cex.axis = 1.2, cex.lab = 1.2)
points(Kerr_fig5$Mass ~ Kerr_fig5$predMass, col = "black", pch = 16, cex = 1.5)

# compute correlation coefficient and root mean square deviation
r <- cor(Kerr_fig5$Mass, Kerr_fig5$predMass)
p <- cor.test(Kerr_fig5$Mass, Kerr_fig5$predMass)$p.value
rmsd <- sqrt(mean(((Kerr_fig5$Mass-Kerr_fig5$predMass) ^ 2),na.rm = TRUE))

# append to plot
text(390 + 9.5,590, "   r     rmsd   p")
text(380 + 8.5,580, paste0('  ', round(r, 3),'   ',round(rmsd, 2),'  ', round(p, 3)))
```

## References

Kerr, G. D., and C. M. Bull. 2004. Field observations of extended locomotor activity at sub-optimal body temperatures in a diurnal heliothermic lizard (Tiliqua rugosa). Journal of Zoology 264:179-188.