---
title: "Create Figure 10 - sample weight and lenght trajectories"
author: "Michael Kearney"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true
classoption: landscape
vignette: >
  %\VignetteIndexEntry{Create Figure 10 - sample weight and lenght trajectories}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(
 eval = TRUE, tidy.opts=list(width.cutoff=60), tidy=TRUE  
)
```

## Overview

This document runs a simulation of the full mechanistic sleepy lizard model under the scenario of water-limitation (water only from food and rainfall) and unlimited water (e.g. near a permanently filled dam). It compares the results to observed body mass and length of the 29 most frequently recorded lizards in Mike Bull's long-term mark-recapture study (50 or more records) (Bull 1987; Bull 1995). The starting date and initial conditions are adjusted to best match the trajectories.

## Setup for the microclimate model

First load the necessary packages and functions.

```{r, echo = FALSE}
library(NicheMapR)
library(raster)
library(dismo)
library(knitr)
source('addTrans.R') # function for making transparent plots
source('plot_growth.R')
source('run_year.R')
source('simliz.R')
```

Choose site to simulate.

```{r, echo = FALSE, message = FALSE, warning = FALSE}
spatial <- "w:/"
longlat <- c(139.3109, -33.888) # Bundey Bore study site
loc <- longlat
```

Specify the years to simulate

```{r, echo = FALSE, message = FALSE, warning = FALSE}
ystart <- 1971# start year
yfinish <- 2014# end year
nyears <- yfinish - ystart + 1# integer, number of years for which to run the microclimate model
```

Load microclimate data and alter underground humidity to better simulate a wombat burrow.

```{r, echo = FALSE, message = FALSE, warning = FALSE}
load('microclimate/micro_1971_2015.Rda')
sat <- WETAIR(db = micro$soil[,3:12])$esat # saturated soil vapour pressure
vpres_soil <- sat * micro$humid[,3:12] # vapour pressure in soil
e <- WETAIR(db = micro$metout[,3], rh = micro$metout[,5])$e # ambient vapour pressure (soil surface)
satmean <- vpres_soil # matrix for weighted mean vapour pressure
weights <- seq(0, .9, .1) # assume linear weighting, with ambient at surface (i.e. start at 0)
#plot(weights~micro$DEP)
satmean <- t(apply(cbind(e, e, e, e, e, e, e, e, e, e), 1, function(x) x * (1 - weights))) + t(apply(vpres_soil, 1, function(x) x * weights)) # get weighted mean vapour pressure
newRH<-satmean / sat # compute relative humidity
newRH[newRH > 1] <- 1 # remove RH > 1
micro$humid[, 3:12] <- newRH # replace values in original soil humidity matrix

sat <- WETAIR(db = micro$shadsoil[, 3:12])$esat # saturated soil vapour pressure
vpres_soil <- sat * micro$shadhumid[, 3:12] # vapour pressure in soil
e <- WETAIR(db = micro$shadmet[,3], rh = micro$shadmet[,5])$e # ambient vapour pressure (soil surface)
satmean <- vpres_soil # matrix for weighted mean vapour pressure
weights <- seq(0, .9, .1) # assume linear weighting, with ambient at surface (i.e. start at 0)
satmean <- t(apply(cbind(e, e, e, e, e, e, e, e, e, e), 1, function(x) x * (1 - weights))) + t(apply(vpres_soil, 1, function(x) x * weights)) # get weighted mean vapour pressure
newRH <- satmean / sat # compute relative humidity
newRH[newRH > 1] <- 1 # remove RH > 1
micro$shadhumid[, 3:12] <- newRH # replace values in original soil humidity matrix
micro$metout[, 10] <- 0
micro$shadmet[, 10] <- 0
micro_all <- micro
```

## Setup for the ectotherm model

Morphology

```{r}
ABSMAX <- 0.866 # maximum solar absorbtivity (dec %), Christian et al. 1996
ABSMIN <- 0.866 # minimum solar absorbtivity (dec %), Christian et al. 1996
EMISAN <- 1 # emissivity
```

Thermal physiology and behaviour.

```{r, echo = FALSE}
TEMERGE <- 8.5 # min Tb at which they will attempt to leave retreat, from Kerr and Bull (2004)
TBASK <- 26 # min Tb at which leaves retreat, from Pamula (1997) Table 3.14
VTMIN <- 26 # minimum Tb at which activity occurs, from Pamula (1997) Table 3.42
VTMAX <- 39 # maximum Tb at which activity occurs, from Pamula (1997) Table 3.42
TPREF <- 33.5 # preferred Tb (will try and regulate to this), from Pamula (1997) Table 3.14
ctmax <- 39 # critical thermal minimum - set to same as VTmax
ctmin <- 3.5 # critical thermal maximum, from Bennet and John-Alder (1986)
maxshades <- micro$MAXSHADES # maximum shade allowed
mindepth <- 3 # min depth (node, 1-10) allowed
shdburrow <- 1 # use shady retreats only in hot weather
```

DEB model settings.

```{r, echo = FALSE}
# load the estimated DEB pars from the estimation procedure previously run in matlab.
debpars <- as.data.frame(read.csv('DEB model/DEB_pars_Tiliqua_rugosa.csv', header = FALSE))$V1 # read in DEB pars
load('feedpars.Rda') # read in feeding parameters from 'Sleepy lizard functional response.Rmd' analysis

# set core parameters
DEB <- 1
z <- debpars[8] # zoom factor (cm)
F_m <- feedpars[2] # max spec searching rate (J/h.cm^2)
kap_X <- debpars[11] # digestion efficiency of food to reserve (-)
v <- debpars[13]/24 # energy conductance (cm/h)
kap <- debpars[14] # kappa, fraction of mobilised reserve to growth/maintenance (-)
kap_R <- debpars[15] # reproduction efficiency (-)
p_M <- debpars[16]/24 # specific somatic maintenance (J/cm3)
k_J <- debpars[18]/24 # maturity maint rate coefficient (1/h)
E_G <- debpars[19] # specific cost for growth (J/cm3)
E_Hb <- debpars[20] # maturity at birth (J)
E_Hp <- debpars[21] # maturity at puberty (J)
h_a <- debpars[22]*10^-2/(24^2) # Weibull aging acceleration (1/h^2)
s_G <- debpars[23] # Gompertz stress coefficient (-)
fract <- 1 # fraction by which zoom factor is changed - genetic difference in size

# set thermal respose curve paramters
T_REF <- debpars[1]-273
TA <- debpars[2] # Arrhenius temperature (K)
TAL <- debpars[5] # low Arrhenius temperature (K)
TAH <- debpars[6] # high Arrhenius temperature (K)
TL <- debpars[3] # low temp boundary (K)
TH <- debpars[4] # hight temp boundary (K)

# set auxiliary parameters
del_M <- debpars[9] # shape coefficient (-) 
E_0 <- debpars[24] # energy of an egg (J)
mu_E <- 585000 # molar Gibbs energy (chemical potential) of reserve (J/mol)

# set initial state
stage <- 1 # initial stage
E_init <- ((debpars[16]/24)*debpars[8]/debpars[14])/(debpars[13]/24) # initial reserve
E_H_init <- debpars[20]+5 # initial maturity
v_init <- debpars[25]^3 # initial structure

# reproduction parameters
clutch_ab <- c(0.085,0.7)#c(0.085,0.7) # paramters for relationship between length (cm) and clutch size: clutch size = a*SVL-b
viviparous <- 1 # yes
photostart <- 4 # vernal equinox
clutchsize <- 2 #
ma <- log(0.915)/-1317 # Jones et al. 2016 annual survival for adults is 0.915, annual act is 1317 on average 
mh <- 1#0.342 # survivorship of hatchling in first year, Jones et al. 2016
  
# water and food budget.
gutfill <- 75 # Gut fill (%) at which satiation occurs - if greater than 100%, animal always tries to forage
raindrink <- 3.51 # mm rain that must fall in a day before rehydration from drinking rainwater occurs
peyes <- 0.03 # of surface area taken up by open eye, for computing ocular water loss (only when active)
ptcond <- 0.1 # dec %, proportion of the body contacting the ground
load('ewl.summary.Rda')
skinwet <- mean(ewl.summary$skinwet[1:3]) # skin wetness at Tb = 25 deg C
skinwet <- mean(ewl.summary$skinwet[c(1:3,7:9,13:15,19:21)]) # skin wetness at Tb = 25 deg C
minwater <- 20 # Minimum tolerated dehydration (% of wet mass) - prohibits foraging if greater than this
aestdepth <- 8 # node to which animals retreate to aestivate when desiccated to 'minwater' level, 8 = 60 cm
plantsim <- c(4, 4, 14, -200, -1500, 82, 1)
E_sm <- feedpars[4] # maximum stomach energy content, J / cm3 structure
K <- feedpars[3] # half saturation constant (#/cm2)
X <- feedpars[1]#111.7/10 # food density (J/cm2)
startday <- 3*30 # day at which simulation starts, i.e. when hatchling emerges
aestivate <- 1
depress <- 0.46
```

## Get observations

```{r, echo = FALSE}
library(foreign)
sleepydata <- read.spss('mark recapture/MMW82-13 6314.SAV', to.data.frame = TRUE)
sleepydata$date <- as.POSIXct(paste(sleepydata$DAY, sleepydata$MNTH, sleepydata$YEAR, sep = '-'), format = "%d-%m-%Y")
sleepydata <- subset(sleepydata, WGT < 1500 & LIZN < 9999)
sleepydata$LGTH[sleepydata$LGTH>50 & is.na(sleepydata$LGTH)==FALSE] <- sleepydata$LGTH[sleepydata$LGTH>50 & is.na(sleepydata$LGTH)==FALSE] / 10
sleepydata$LGTH[sleepydata$LGTH>50 & is.na(sleepydata$LGTH)==FALSE] <- sleepydata$LGTH[sleepydata$LGTH>50 & is.na(sleepydata$LGTH)==FALSE] / 10
trim <- function (x) gsub("^\\s+|\\s+$", "", x)
sleepydata$LIZN <- trim(sleepydata$LIZN)
sleepydata$SEX <- trim(sleepydata$SEX)
lizards <- unique(sleepydata$LIZN)

xlims <- c(min(sleepydata$date, na.rm = TRUE), max(sleepydata$date, na.rm = TRUE))
wgtlims <- c(min(sleepydata$WGT, na.rm = TRUE), max(sleepydata$WGT, na.rm = TRUE))
lenlims <- c(min(sleepydata$LGTH, na.rm = TRUE), max(sleepydata$LGTH, na.rm = TRUE))

liznums <- aggregate(sleepydata$LIZN, by = list(sleepydata$LIZN), FUN = length)
liznums <- liznums[order(liznums$x, decreasing = TRUE),]
liznums <- subset(liznums, x > 50)
```

\newpage

## Lizards 2013 * 3989

```{r, fig.width = 15, fig.height = 11, echo = FALSE, message = FALSE, warning = FALSE}
simliz(yrstrt = 1, yrstrt2 = 1, lizard = 2013, init = 3, init2 = 3, limx = 0) # lizard to do

simliz(yrstrt = 5, yrstrt2 = 16, lizard = 3989, init = 1, init2 = 1, limx = 0) # lizard to do
```

