---
title: "Simulation tests of weather, soil temperature, and great desert skink burrow temperature and humidity at Newhaven Sanctuary 2013/2014"
author: "Michael Kearney"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{Simulation tests of weather, soil temperature, and great desert skink burrow temperature and humidity at Newhaven Sanctuary 2013/2014}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
 eval = TRUE, tidy.opts=list(width.cutoff=60), tidy=TRUE  
)
```

## Overview

This document compares simulatd weather conditions (air temperature, wind speed, relative humidity and solar radiation - measured by a Campbell's Weatherhawk), as well as soil temperature and burrow temperature and relative humidity, to those measured by Danae Moore and Joe Schofield in 2013/14 at Newhaven Wildlife Sanctuary as part of an external Great Desert Skink research project.


```{r, warning = FALSE, message = FALSE}
library(NicheMapR)
library(dplyr)
```

## Run the model with daily gridded data for Australia

Run the model using historical daily gridded data for Australia from 2013 to 2014.

First set up some soil properties for the site.

```{r, warning = FALSE, message = FALSE}
#source("c:/git/micro_australia/get.soil.R")
ystart <- 2013# start year
yfinish <- 2014# end year
nyears<-yfinish-ystart+1# integer, number of years for which to run the microclimate model
loc <- c(131.183806, -22.797235)
longlat <- rbind(loc)
```

Now set the soil properties. First retrieve soil properties from Soil and Landscape Grid of Australia (SLGA)

```{r, eval=TRUE, warning = FALSE, message = FALSE}
prevdir<-getwd()
setwd('x:')
cmd<-paste("R --no-save --args ",longlat[1]," ",longlat[2]," < extract.R",sep='')
system(cmd)
soilpro<-read.csv('data.csv')
setwd(prevdir)
soilpro[,1]<-c(2.5,7.5,22.5,45,80,150)
colnames(soilpro)[1] <- 'depth'
```

Now get hydraulic properties for this soil using Cosby et al. 1984 pedotransfer functions.

```{r, eval=TRUE, warning = FALSE, message = FALSE}
DEP <- c(0., 1.,  3, 5.,  10,  15,  30.,  60.,  100.,  200.) # Soil nodes (cm)
soil.hydro<-pedotransfer(soilpro = as.data.frame(soilpro), DEP = DEP)
PE<-soil.hydro$PE
BB<-soil.hydro$BB
BD<-soil.hydro$BD
KS<-soil.hydro$KS
BD[1:9]<-BD[1:9]#*1.7 # make top 15 cm more dense
BulkDensity <- BD[seq(1,19,2)]*1000 #soil bulk density, kg/m3
```

Get qualitative soil type out of interest.

```{r, eval=TRUE, warning = FALSE, message = FALSE}
# search through observed textures and find the nearest match to Campell and Norman's Table 9.1
stypes<-NULL
for(m in 1:nrow(soilpro)){
 ssq<-(CampNormTbl9_1[,2]-soilpro[m,4]/100)^2 + (CampNormTbl9_1[,3]-soilpro[m,3]/100)^2
 stypes[m]<-which(ssq==min(ssq))
}

# produce a table of the qualitative soil profile
soils<-as.character(CampNormTbl9_1[,1])
profile<-as.data.frame(cbind(soilpro[,1],soils[stypes]), stringsAsFactors=FALSE)
profile[,1]<-as.numeric(profile[,1])
colnames(profile)<-c("depth","soiltype")
library(knitr)
kable(profile)
``` 

Get Leaf Area Index estimate

```{r, eval=FALSE, warning = FALSE, message = FALSE}
library(raster)
monthly_LAI <- stack("W:/monthlyLAI.nc")
lonlat<-as.data.frame(longlat)
monthly_LAI <- crop(monthly_LAI, extent(lonlat[1,1]-0.1, lonlat[1,1]+0.1, lonlat[1,2]-0.1, lonlat[1,2]+0.1))
LAI_month<-extract(monthly_LAI, cbind(longlat[1],longlat[2]))
juldays12 <- c(15, 46, 74, 105, 135, 166, 196, 227, 258, 288, 319, 349)
LAI <- suppressWarnings(spline(juldays12, LAI_month, n = 365, xmin = 1, xmax = 365, method = "periodic"))$y
LAI <- rep(LAI, nyears)
```

Now run the microclimate model and get the output.

```{r, eval=FALSE, warning = FALSE, message = FALSE}
micro<-micro_aust(loc = loc, maxshade = 70, ystart = ystart, yfinish = yfinish, PE = PE, BB = BB, BD = BD, KS = KS, BulkDensity = BulkDensity, spatial = "w:/", windfac = 1, LAI = LAI, cap = 0, TIMAXS = c(2, 1, 0, 0))
save(micro, file = "c:/Users/mrke/My Dropbox/Current Research Projects/Tiliqua rugosa/micro_Newhaven.Rda")
```

Estimate burrow humidity from weighted average vapour pressure between near-surface and soil

```{r, warning = FALSE, message = FALSE}
load("c:/Users/mrke/My Dropbox/Current Research Projects/Tiliqua rugosa/micro_Newhaven.Rda")

sat<-WETAIR(db = micro$soil[,3:12])$esat # saturated soil vapour pressure
vpres_soil<-sat * micro$humid[,3:12] # vapour pressure in soil
e<-WETAIR(db = micro$metout[,3], rh = micro$metout[,5])$e # ambient vapour pressure (soil surface)
satmean <- vpres_soil # matrix for weighted mean vapour pressure
weights <- seq(0, .9, .1) # assume linear weighting, with ambient at surface (i.e. start at 0)
satmean <- t(apply(cbind(e, e, e, e, e, e, e, e, e, e), 1, function(x) x * (1 - weights))) + t(apply(vpres_soil, 1, function(x) x * weights)) # get weighted mean vapour pressure
newRH<-satmean / sat # compute relative humidity
newRH[newRH > 1] <- 1 # remove RH > 1
micro$humid[ ,3:12] <- newRH # replace values in original soil humidity matrix
```

Next, append dates

```{r, warning = FALSE, message = FALSE}
tzone=paste("Etc/GMT-",10,sep="") # doing it this way ignores daylight savings!
dates=seq(ISOdate(ystart,1,1,tz=tzone)-3600*12, ISOdate((ystart+nyears),1,1,tz=tzone)-3600*13, by="hours")
dates=subset(dates, format(dates, "%m/%d")!= "02/29") # remove leap years
dates2=seq(ISOdate(ystart,1,1,tz=tzone)-3600*12, ISOdate((ystart+nyears),1,1,tz=tzone)-3600*13, by="days") 
dates2=subset(dates2, format(dates2, "%m/%d")!= "02/29") # remove leap years

metout <- as.data.frame(cbind(dates,as.data.frame(micro$metout))) # above ground microclimatic conditions, min shade
soil <- as.data.frame(cbind(dates,as.data.frame(micro$soil))) # soil temperatures, minimum shade
humid <- as.data.frame(cbind(dates,as.data.frame(micro$humid))) # soil temperatures, minimum shade
```


## Compare with measurements

Read in copper model data and format dates.

```{r, warning = FALSE, message = FALSE, include=TRUE}
gds_dir <- "c:/Users/mrke/My Dropbox/Student Projects/gds/"

# read in soil data
obs.surfaces <- read.csv(paste0(gds_dir, "csv summaries/all.soil.surfaces.csv"), stringsAsFactors = FALSE)[,-1]
obs.5cms <- read.csv(paste0(gds_dir, "csv summaries/all.soil.5cms.csv"), stringsAsFactors = FALSE)[,-1]
obs.15cms <- read.csv(paste0(gds_dir, "csv summaries/all.soil.15cms.csv"), stringsAsFactors = FALSE)[,-1]
obs.30cms <- read.csv(paste0(gds_dir, "csv summaries/all.soil.30cms.csv"), stringsAsFactors = FALSE)[,-1]
obs.50cms <- read.csv(paste0(gds_dir, "csv summaries/all.soil.50cms.csv"), stringsAsFactors = FALSE)[,-1]
obs.1ms <- read.csv(paste0(gds_dir, "csv summaries/all.soil.1ms.csv"), stringsAsFactors = FALSE)[,-1]

# read in burrow data
obs.burrow.surf <- read.csv(paste0(gds_dir, "csv summaries/all.burrow.surf.csv"), stringsAsFactors = FALSE)[,-1]
obs.burrow.mid <- read.csv(paste0(gds_dir, "csv summaries/all.burrow.mid.csv"), stringsAsFactors = FALSE)[,-1]
obs.burrow.deep <- read.csv(paste0(gds_dir, "csv summaries/all.burrow.deep.csv"), stringsAsFactors = FALSE)[,-1]
```

Plot observed and predicted values for weather station data, as well as model fit statistics

\newpage

```{r, echo = FALSE, warning = FALSE, message = FALSE, include=TRUE, fig.width = 7, fig.height = 4.5}

source('addTrans.R') # function for making transparent plots

# choose time period to plot
xlims <- c(as.POSIXct("2013-10-01 00:00:00", format = "%Y-%m-%d %H:%M:%S"), as.POSIXct("2014-09-30 00:00:00", format = "%Y-%m-%d %H:%M:%S"))

# read in weather data
weather_obs <- read.csv(paste0(gds_dir,"csv summaries/weather_obs.csv"), stringsAsFactors = FALSE)[,-1]
weather_obs$TIMESTAMP <- as.POSIXct(weather_obs$TIMESTAMP, format = "%Y-%m-%d %H:%M:%S")
weather_obs$TIMESTAMP <- weather_obs$TIMESTAMP - 30*60 # central standard time

# get hourly means from weather_obs and merge with metout
weather_obs_hrly <- aggregate(weather_obs, by = list(format(weather_obs$TIMESTAMP, "%Y-%m-%d %H")), FUN = mean)
metout$Group.1 <- format(metout$dates, "%Y-%m-%d %H")
metout_weather <- merge(metout, weather_obs_hrly, all.x = TRUE)

# plot air temperature test results

plot(metout_weather$dates, metout_weather$TAREF, main='1.2 m weather station air temperature', type = 'l', xlim = xlims, ylim = c(-10,70), ylab = bquote(paste(.(1.2), ' m', ' air temperature (', ~degree~C,')')), xlab ='date')
lines(metout_weather$dates, metout_weather$AirTemp_C_Avg, col = addTrans("red",150))

# get fit of air temperature predictions and plot
weather_obs_pred <- subset(metout_weather, is.na(metout_weather$AirTemp_C_Avg) == FALSE)
r<-cor(weather_obs_pred$TAREF,weather_obs_pred$AirTemp_C_Avg)
rmsd = sqrt(mean(((weather_obs_pred$TAREF-weather_obs_pred$AirTemp_C_Avg)^2),na.rm=TRUE))

x = -10:50
plot(x,x, type = 'l', main='model fit', ylab = bquote(paste('observed (', ~degree~C,')')), xlab = bquote(paste('predicted (', ~degree~C,')')))
points(weather_obs_pred$TAREF,weather_obs_pred$AirTemp_C_Avg, col=addTrans("black",50), pch = 16)
text(4.5+6.5,46, "         r     rmsd")
text(3+5,42, paste0('model fit ',round(r,3),'   ',round(rmsd,2)))

# plot wind speed test results

plot(metout_weather$dates, metout_weather$VREF, main='1.2 m weather station wind speed', type = 'l', xlim = xlims, ylim = c(0,10), ylab = "wind speed, m/s", xlab ='date')
lines(metout_weather$dates, metout_weather$WindSpeed_ms_Avg, col = addTrans("red",150))

# get fit of wind predictions and plot
weather_obs_pred <- subset(metout_weather, is.na(metout_weather$WindSpeed_ms_Avg) == FALSE)
r<-cor(weather_obs_pred$VREF,weather_obs_pred$WindSpeed_ms_Avg)
rmsd = sqrt(mean(((weather_obs_pred$VREF-weather_obs_pred$WindSpeed_ms_Avg)^2),na.rm=TRUE))

x = 0:9
plot(x,x, type = 'l', main='model fit', ylab = "observed, m/s", xlab = "predicted,  m/s")
points(weather_obs_pred$VREF,weather_obs_pred$WindSpeed_ms_Avg, col=addTrans("black",50), pch = 16)
text(2.5,9, "         r     rmsd")
text(2,8.3, paste0('model fit ',round(r,3),'   ',round(rmsd,2)))

# plot relative humidity test results

plot(metout_weather$dates, metout_weather$RH, main='1.2 m weather station relative humidity', type = 'l', xlim = xlims, ylim = c(0,100), ylab = "relative humidity, %", xlab ='date')
lines(metout_weather$dates, metout_weather$RH_Avg, col = addTrans("red",150))

# get fit of wind predictions and plot
weather_obs_pred <- subset(metout_weather, is.na(metout_weather$RH_Avg) == FALSE)
r<-cor(weather_obs_pred$RH,weather_obs_pred$RH_Avg)
rmsd = sqrt(mean(((weather_obs_pred$RH-weather_obs_pred$RH_Avg)^2),na.rm=TRUE))

x = 0:100
plot(x,x, type = 'l', main='model fit', ylab = "observed,  %", xlab = "predicted,  %")
points(weather_obs_pred$RH,weather_obs_pred$RH_Avg, col=addTrans("black",50), pch = 16)
text(17,90, "         r     rmsd")
text(12.5,83, paste0('model fit ',round(r,3),'   ',round(rmsd,2)))

# plot solar radiation test results

plot(metout_weather$dates, metout_weather$SOLR, main='weather station solar radiation', type = 'l', xlim = xlims, ylim = c(0,1200), ylab = "solar radiation, W/m2", xlab ='date')
lines(metout_weather$dates, metout_weather$Solar_Avg, col = addTrans("red",150))

# get fit of solar radiation predictions and plot
weather_obs_pred <- subset(metout_weather, is.na(metout_weather$Solar_Avg) == FALSE)
r<-cor(weather_obs_pred$SOLR,weather_obs_pred$Solar_Avg)
rmsd = sqrt(mean(((weather_obs_pred$SOLR-weather_obs_pred$Solar_Avg)^2),na.rm=TRUE))

x = 0:1200
plot(x,x, type = 'l', main='model fit', ylab = "observed,  W/m2", xlab = "predicted,  W/m2")
points(weather_obs_pred$SOLR,weather_obs_pred$Solar_Avg, col=addTrans("black",50), pch = 16)
text(190,1000, "         r     rmsd")
text(135,900, paste0('model fit ',round(r,3),'   ',round(rmsd,2)))

#  surface soil temperature test

# merge
D0cm <- obs.surfaces
D0cm$date_time <- as.POSIXct(D0cm$date_time, format = "%Y-%m-%d %H:%M:%S")
D0cm <- aggregate(D0cm, by = list(format(D0cm$date_time, "%Y-%m-%d %H")), FUN = mean)
soil2 <- soil
soil2$Group.1 <- format(soil2$dates, "%Y-%m-%d %H")
D0cm_obs.pred <- merge(soil2, D0cm, all.x = TRUE)

# plot surface soil temperature test results

plot(D0cm_obs.pred$dates, D0cm_obs.pred$D0cm, main='surface soil temperature', type = 'l', xlim = xlims, ylim = c(-10,70), ylab = bquote(paste('temperature (', ~degree~C,')')), xlab ='date')
lines(D0cm_obs.pred$dates, D0cm_obs.pred$temperature, col = addTrans("red",150))

# get fit of D0cm predictions and plot
D0cm_obs_pred <- subset(D0cm_obs.pred, is.na(D0cm_obs.pred$temperature) == FALSE)
r<-cor(D0cm_obs_pred$D0cm,D0cm_obs_pred$temperature)
rmsd = sqrt(mean(((D0cm_obs_pred$D0cm-D0cm_obs_pred$temperature)^2),na.rm=TRUE))

x = -10:70
plot(x,x, type = 'l', main='model fit', ylab = bquote(paste('observed (', ~degree~C,')')), xlab = bquote(paste('predicted (', ~degree~C,')')))
points(D0cm_obs.pred$D0cm,D0cm_obs.pred$temperature, col=addTrans("black",50), pch = 16)
text(4.5+6.5,46, "         r     rmsd")
text(3+5,40, paste0('model fit ',round(r,3),'   ',round(rmsd,2)))

# 5cm soil temperature test

# merge
D5cm <- obs.5cms
D5cm$date_time <- as.POSIXct(D5cm$date_time, format = "%Y-%m-%d %H:%M:%S")
D5cm <- aggregate(D5cm, by = list(format(D5cm$date_time, "%Y-%m-%d %H")), FUN = mean)
soil2 <- soil
soil2$Group.1 <- format(soil2$dates, "%Y-%m-%d %H")
D5cm_obs.pred <- merge(soil2, D5cm, all.x = TRUE)

# plot 5cm soil temperature test results

plot(D5cm_obs.pred$dates, D5cm_obs.pred$D5cm, main='5cm soil temperature', type = 'l', xlim = xlims, ylim = c(-10,70), ylab = bquote(paste('temperature (', ~degree~C,')')), xlab ='date')
lines(D5cm_obs.pred$dates, D5cm_obs.pred$temperature, col = addTrans("red",150))

# get fit of 5cm predictions and plot
D5cm_obs_pred <- subset(D5cm_obs.pred, is.na(D5cm_obs.pred$temperature) == FALSE)
r<-cor(D5cm_obs_pred$D5cm,D5cm_obs_pred$temperature)
rmsd = sqrt(mean(((D5cm_obs_pred$D5cm-D5cm_obs_pred$temperature)^2),na.rm=TRUE))

x = -10:70
plot(x,x, type = 'l', main='model fit', ylab = bquote(paste('observed (', ~degree~C,')')), xlab = bquote(paste('predicted (', ~degree~C,')')))
points(D5cm_obs.pred$D5cm,D5cm_obs.pred$temperature, col=addTrans("black",50), pch = 16)
text(4.5+6.5,46, "         r     rmsd")
text(3+5,40, paste0('model fit ',round(r,3),'   ',round(rmsd,2)))

# 15cm soil temperature test

# merge
D15cm <- obs.15cms
D15cm$date_time <- as.POSIXct(D15cm$date_time, format = "%Y-%m-%d %H:%M:%S")
D15cm <- aggregate(D15cm, by = list(format(D15cm$date_time, "%Y-%m-%d %H")), FUN = mean)
soil2 <- soil
soil2$Group.1 <- format(soil2$dates, "%Y-%m-%d %H")
D15cm_obs.pred <- merge(soil2, D15cm, all.x = TRUE)

# plot 15 cm soil temperature test results

plot(D15cm_obs.pred$dates, D15cm_obs.pred$D15cm, main='15cm soil temperature', type = 'l', xlim = xlims, ylim = c(-10,70), ylab = bquote(paste('temperature (', ~degree~C,')')), xlab ='date')
lines(D15cm_obs.pred$dates, D15cm_obs.pred$temperature, col = addTrans("red",150))

# get fit of 15cm predictions and plot
D15cm_obs_pred <- subset(D15cm_obs.pred, is.na(D15cm_obs.pred$temperature) == FALSE)
r<-cor(D15cm_obs_pred$D15cm,D15cm_obs_pred$temperature)
rmsd = sqrt(mean(((D15cm_obs_pred$D15cm-D15cm_obs_pred$temperature)^2),na.rm=TRUE))

x = -10:70
plot(x,x, type = 'l', main='model fit', ylab = bquote(paste('observed (', ~degree~C,')')), xlab = bquote(paste('predicted (', ~degree~C,')')))
points(D15cm_obs.pred$D15cm,D15cm_obs.pred$temperature, col=addTrans("black",50), pch = 16)
text(4.5+6.5,46, "         r     rmsd")
text(3+5,40, paste0('model fit ',round(r,3),'   ',round(rmsd,2)))

# 30cm soil temperature test

# merge
D30cm <- obs.30cms
D30cm$date_time <- as.POSIXct(D30cm$date_time, format = "%Y-%m-%d %H:%M:%S")
D30cm <- aggregate(D30cm, by = list(format(D30cm$date_time, "%Y-%m-%d %H")), FUN = mean)
soil2 <- soil
soil2$Group.1 <- format(soil2$dates, "%Y-%m-%d %H")
D30cm_obs.pred <- merge(soil2, D30cm, all.x = TRUE)

# plot 30cm soil temperature test results

plot(D30cm_obs.pred$dates, D30cm_obs.pred$D30cm, main='30cm soil temperature', type = 'l', xlim = xlims, ylim = c(-10,70), ylab = bquote(paste('temperature (', ~degree~C,')')), xlab ='date')
lines(D30cm_obs.pred$dates, D30cm_obs.pred$temperature, col = addTrans("red",150))

# get fit of 30cm predictions and plot
D30cm_obs_pred <- subset(D30cm_obs.pred, is.na(D30cm_obs.pred$temperature) == FALSE)
r<-cor(D30cm_obs_pred$D30cm,D30cm_obs_pred$temperature)
rmsd = sqrt(mean(((D30cm_obs_pred$D30cm-D30cm_obs_pred$temperature)^2),na.rm=TRUE))

x = -10:70
plot(x,x, type = 'l', main='model fit', ylab = bquote(paste('observed (', ~degree~C,')')), xlab = bquote(paste('predicted (', ~degree~C,')')))
points(D30cm_obs.pred$D30cm,D30cm_obs.pred$temperature, col=addTrans("black",50), pch = 16)
text(4.5+6.5,46, "         r     rmsd")
text(3+5,40, paste0('model fit ',round(r,3),'   ',round(rmsd,2)))

# plot 50cm soil temperature test results

# merge
D50cm <- obs.50cms
D50cm$date_time <- as.POSIXct(D50cm$date_time, format = "%Y-%m-%d %H:%M:%S")
D50cm <- aggregate(D50cm, by = list(format(D50cm$date_time, "%Y-%m-%d %H")), FUN = mean)
soil2 <- soil
soil2$Group.1 <- format(soil2$dates, "%Y-%m-%d %H")
D50cm_obs.pred <- merge(soil2, D50cm, all.x = TRUE)

# plot 50cm soil temperature test results

plot(D50cm_obs.pred$dates, D50cm_obs.pred$D50cm, main='50cm soil temperature', type = 'l', xlim = xlims, ylim = c(-10,70), ylab = bquote(paste('temperature (', ~degree~C,')')), xlab ='date')
lines(D50cm_obs.pred$dates, D50cm_obs.pred$temperature, col = addTrans("red",150))

# get fit of 50cm predictions and plot
D50cm_obs_pred <- subset(D50cm_obs.pred, is.na(D50cm_obs.pred$temperature) == FALSE)
r<-cor(D50cm_obs_pred$D50cm,D50cm_obs_pred$temperature)
rmsd = sqrt(mean(((D50cm_obs_pred$D50cm-D50cm_obs_pred$temperature)^2),na.rm=TRUE))

x = -10:70
plot(x,x, type = 'l', main='model fit', ylab = bquote(paste('observed (', ~degree~C,')')), xlab = bquote(paste('predicted (', ~degree~C,')')))
points(D50cm_obs.pred$D50cm,D50cm_obs.pred$temperature, col=addTrans("black",50), pch = 16)
text(4.5+6.5,46, "         r     rmsd")
text(3+5,40, paste0('model fit ',round(r,3),'   ',round(rmsd,2)))

# soil 100cm test

# merge
D100cm <- obs.1ms
D100cm$date_time <- as.POSIXct(D100cm$date_time, format = "%Y-%m-%d %H:%M:%S")
D100cm <- aggregate(D100cm, by = list(format(D100cm$date_time, "%Y-%m-%d %H")), FUN = mean)
soil2 <- soil
soil2$Group.1 <- format(soil2$dates, "%Y-%m-%d %H")
D100cm_obs.pred <- merge(soil2, D100cm, all.x = TRUE)

# plot 100cm soil temperature test results

plot(D100cm_obs.pred$dates, D100cm_obs.pred$D100cm, main='100cm soil temperature', type = 'l', xlim = xlims, ylim = c(-10,70), ylab = bquote(paste('temperature (', ~degree~C,')')), xlab ='date')
lines(D100cm_obs.pred$dates, D100cm_obs.pred$temperature, col = addTrans("red",150))

# get fit of 100cm predictions and plot
D100cm_obs_pred <- subset(D100cm_obs.pred, is.na(D100cm_obs.pred$temperature) == FALSE)
r<-cor(D100cm_obs_pred$D100cm,D100cm_obs_pred$temperature)
rmsd = sqrt(mean(((D100cm_obs_pred$D100cm-D100cm_obs_pred$temperature)^2),na.rm=TRUE))

x = -10:70
plot(x,x, type = 'l', main='model fit', ylab = bquote(paste('observed (', ~degree~C,')')), xlab = bquote(paste('predicted (', ~degree~C,')')))
points(D100cm_obs.pred$D100cm,D100cm_obs.pred$temperature, col=addTrans("black",50), pch = 16)
text(4.5+6.5,46, "         r     rmsd")
text(3+5,40, paste0('model fit ',round(r,3),'   ',round(rmsd,2)))

# surface burrow temperature test

# merge
surf <- obs.burrow.surf
surf$date_time <- as.POSIXct(surf$date_time, format = "%Y-%m-%d %H:%M:%S")
surf$date_time <- surf$date_time - 30 * 60
surf <- aggregate(surf, by = list(format(surf$date_time, "%Y-%m-%d %H")), FUN = mean)
soil2 <- soil
soil2$Group.1 <- format(soil2$dates, "%Y-%m-%d %H")
surf_obs.pred <- merge(soil2, surf, all.x = TRUE)

# plot surface burrow temperature test results

plot(surf_obs.pred$dates, surf_obs.pred$D10cm, main='surface burrow temperature', type = 'l', xlim = xlims, ylim = c(-10,60), ylab = bquote(paste('temperature (', ~degree~C,')')), xlab ='date')
lines(surf_obs.pred$dates, surf_obs.pred$temperature, col = addTrans("red",150))

# get fit of surface predictions and plot
surf_obs_pred <- subset(surf_obs.pred, is.na(surf_obs.pred$temperature) == FALSE)
r<-cor(surf_obs_pred$D10cm,surf_obs_pred$temperature)
rmsd = sqrt(mean(((surf_obs_pred$D10cm-surf_obs_pred$temperature)^2),na.rm=TRUE))

x = -10:60
plot(x,x, type = 'l', ylab = bquote(paste('observed (', ~degree~C,')')), xlab = bquote(paste('predicted (', ~degree~C,')')))
points(surf_obs_pred$D10cm,surf_obs_pred$temperature, col=addTrans("black",50), pch = 16)
text(7+6.5,46, "         r     rmsd")
text(6+5,40, paste0('model fit ',round(r,3),'   ',round(rmsd,2)))

# mid burrow temperature test

# merge
mid <- obs.burrow.mid
mid$date_time <- as.POSIXct(mid$date_time, format = "%Y-%m-%d %H:%M:%S")
mid$date_time <- mid$date_time - 30 * 60
mid <- aggregate(mid, by = list(format(mid$date_time, "%Y-%m-%d %H")), FUN = mean)
soil2 <- soil
soil2$Group.1 <- format(soil2$dates, "%Y-%m-%d %H")
mid_obs.pred <- merge(soil2, mid, all.x = TRUE)

# plot mid burrow temperature test results

plot(mid_obs.pred$dates, mid_obs.pred$D30cm, main='mid burrow temperature', type = 'l', xlim = xlims, ylim = c(-10,60), ylab = bquote(paste('temperature (', ~degree~C,')')), xlab ='date')
lines(mid_obs.pred$dates, mid_obs.pred$temperature, col = addTrans("red",150))

# get fit of mid burrow predictions and plot
mid_obs_pred <- subset(mid_obs.pred, is.na(mid_obs.pred$temperature) == FALSE)
r<-cor(mid_obs_pred$D30cm,mid_obs_pred$temperature)
rmsd = sqrt(mean(((mid_obs_pred$D30cm-mid_obs_pred$temperature)^2),na.rm=TRUE))

x = -10:60
plot(x,x, type = 'l', main='model fit', ylab = bquote(paste('observed (', ~degree~C,')')), xlab = bquote(paste('predicted (', ~degree~C,')')))
points(mid_obs_pred$D30cm,mid_obs_pred$temperature, col=addTrans("black",50), pch = 16)
text(7+6.5,46, "         r     rmsd")
text(6+5,40, paste0('model fit ',round(r,3),'   ',round(rmsd,2)))

# deep burrow temperature test

# merge
deep <- obs.burrow.deep
deep$date_time <- as.POSIXct(deep$date_time, format = "%Y-%m-%d %H:%M:%S")
deep$date_time <- deep$date_time - 30 * 60
deep <- aggregate(deep, by = list(format(deep$date_time, "%Y-%m-%d %H")), FUN = mean)
soil2 <- soil
soil2$Group.1 <- format(soil2$dates, "%Y-%m-%d %H")
deep_obs.pred <- merge(soil2, deep, all.x = TRUE)

# plot deep burrow temperature test results

plot(deep_obs.pred$dates, deep_obs.pred$D50cm, main='deep burrow temperature', type = 'l', xlim = xlims, ylim = c(-10,60), ylab = bquote(paste('temperature (', ~degree~C,')')), xlab ='date')
lines(deep_obs.pred$dates, deep_obs.pred$temperature, col = addTrans("red",150))

# get fit of deep burrow predictions and plot
deep_obs_pred <- subset(deep_obs.pred, is.na(deep_obs.pred$temperature) == FALSE)
r<-cor(deep_obs_pred$D50cm,deep_obs_pred$temperature)
rmsd = sqrt(mean(((deep_obs_pred$D50cm-deep_obs_pred$temperature)^2),na.rm=TRUE))

x = -10:60
plot(x,x, type = 'l', main='model fit', ylab = bquote(paste('observed (', ~degree~C,')')), xlab = bquote(paste('predicted (', ~degree~C,')')))
points(deep_obs_pred$D50cm,deep_obs_pred$temperature, col=addTrans("black",50), pch = 16)
text(7+6.5,46, "         r     rmsd")
text(6+5,40, paste0('model fit ',round(r,3),'   ',round(rmsd,2)))

# surface burrow humidity test

humid2 <- humid
humid2[,4:13] <- humid2[,4:13] * 100
humid2$Group.1 <- format(humid2$dates, "%Y-%m-%d %H")
surf_obs.pred <- merge(humid2, surf, all.x = TRUE)

# plot surface humidity test results

plot(surf_obs.pred$dates, surf_obs.pred$RH10cm, main='surface burrow humidity', type = 'l', xlim = xlims, ylim = c(0,100), ylab = 'relative humidity (%)', xlab ='date')
lines(surf_obs.pred$dates, surf_obs.pred$humidity, col = addTrans("red",150))

# get fit of surface humidity predictions and plot
surf_obs_pred <- subset(surf_obs.pred, is.na(surf_obs.pred$humidity) == FALSE)
r<-cor(surf_obs_pred$RH10cm,surf_obs_pred$humidity)
rmsd = sqrt(mean(((surf_obs_pred$RH10cm-surf_obs_pred$humidity)^2),na.rm=TRUE))

x = 0:100
plot(x,x, type = 'l', main='model fit',ylab = "observed,  %", xlab = "predicted,  %")
points(surf_obs_pred$RH10cm,surf_obs_pred$humidity, col=addTrans("black",50), pch = 16)
text(9+6.5,96, "         r     rmsd")
text(7.5+5.5,85, paste0('model fit ',round(r,3),'   ',round(rmsd,2)))

# mid burrow humidity test

# merge
mid <- obs.burrow.mid
mid$date_time <- as.POSIXct(mid$date_time, format = "%Y-%m-%d %H:%M:%S")
mid$date_time <- mid$date_time - 30 * 60
mid <- aggregate(mid, by = list(format(mid$date_time, "%Y-%m-%d %H")), FUN = mean)
humid2 <- humid
humid2[,4:13] <- humid2[,4:13] * 100
humid2$Group.1 <- format(humid2$dates, "%Y-%m-%d %H")
mid_obs.pred <- merge(humid2, mid, all.x = TRUE)

# plot mid burrow humidity test results

plot(mid_obs.pred$dates, mid_obs.pred$RH30cm, main='mid burrow humidity', type = 'l', xlim = xlims, ylim = c(0,100), ylab = 'relative humidity (%)', xlab ='date')
lines(mid_obs.pred$dates, mid_obs.pred$humidity, col = addTrans("red",150))

# get fit of mid burrow predictions and plot
mid_obs_pred <- subset(mid_obs.pred, is.na(mid_obs.pred$humidity) == FALSE)
r<-cor(mid_obs_pred$RH30cm,mid_obs_pred$humidity)
rmsd = sqrt(mean(((mid_obs_pred$RH30cm-mid_obs_pred$humidity)^2),na.rm=TRUE))

x = 0:100
plot(x,x, type = 'l', main='model fit', ylab = "observed,  %", xlab = "predicted,  %")
points(mid_obs_pred$RH30cm,mid_obs_pred$humidity, col=addTrans("black",50), pch = 16)
text(9+6.5,96, "         r     rmsd")
text(7.5+5.5,85, paste0('model fit ',round(r,3),'   ',round(rmsd,2)))

# deep burrow humidity test

# merge
deep <- obs.burrow.deep
deep$date_time <- as.POSIXct(deep$date_time, format = "%Y-%m-%d %H:%M:%S")
deep$date_time <- deep$date_time - 30 * 60
deep <- aggregate(deep, by = list(format(deep$date_time, "%Y-%m-%d %H")), FUN = mean)
humid2 <- humid
humid2[,4:13] <- humid2[,4:13] * 100
humid2$Group.1 <- format(humid2$dates, "%Y-%m-%d %H")
deep_obs.pred <- merge(humid2, deep, all.x = TRUE)

# plot deep burrow humidity test results

plot(deep_obs.pred$dates, deep_obs.pred$RH50cm, main='deep burrow humidity', type = 'l', xlim = xlims, ylim = c(0,100), ylab = 'relative humidity (%)', xlab ='date')
lines(deep_obs.pred$dates, deep_obs.pred$humidity, col = addTrans("red",150))

# get fit of deep burrow predictions and plot
deep_obs_pred <- subset(deep_obs.pred, is.na(deep_obs.pred$humidity) == FALSE)
r<-cor(deep_obs_pred$RH50cm,deep_obs_pred$humidity)
rmsd = sqrt(mean(((deep_obs_pred$RH50cm-deep_obs_pred$humidity)^2),na.rm=TRUE))

x = 0:100
plot(x,x, type = 'l', main='model fit', ylab = "observed,  %", xlab = "predicted,  %")
points(deep_obs_pred$RH50cm,deep_obs_pred$humidity, col=addTrans("black",50), pch = 16)
text(9+6.5,96, "         r     rmsd")
text(7.5+5.5,85, paste0('model fit ',round(r,3),'   ',round(rmsd,2)))
```
