---
title: "Simulation tests of burrow temperature and humidity for a Southern Hairy Nosed wombat"
author: "Michael Kearney"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{Simulation tests of burrow temperature and humidity for a Southern Hairy Nosed wombat}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
 eval = TRUE, tidy.opts=list(width.cutoff=60), tidy=TRUE  
)
```

## Overview

This document computes vapour pressure in a burrow in Swan Reach Australia using the weighted average method, to compare with Fig. 8 in Shimmin et al (2002)'s wombat burrow study. Greg Shimmin stated via email 15/3/2017 that the raw data are no longer available.

```{r}
library(NicheMapR)
library(raster)
library(dplyr)
library(scatterplot3d)
library(akima)
library(rgl)
source('addTrans.R')
```

## Run the model with daily gridded data for Australia

Run the model using historical daily gridded data for Australia from 1999 to 2000

First set up some soil properties for the site.

```{r}
#source("c:/git/micro_australia/get.soil.R")
ystart <- 1999# start year
yfinish <- 2000# end year
nyears<-yfinish-ystart+1# integer, number of years for which to run the microclimate model
loc <- c(139.613933, -34.570727)
longlat <- rbind(loc)
```

Now set the soil properties. First retrieve soil properties from Soil and Landscape Grid of Australia (SLGA)

```{r, eval=TRUE}
prevdir<-getwd()
setwd('x:')
cmd<-paste("R --no-save --args ",longlat[1]," ",longlat[2]," < extract.R",sep='')
system(cmd)
soilpro<-read.csv('data.csv')
setwd(prevdir)
soilpro[,1]<-c(2.5,7.5,22.5,45,80,150)
colnames(soilpro)[1] <- 'depth'
```

Now get hydraulic properties for this soil using Cosby et al. 1984 pedotransfer functions.

```{r, eval=TRUE}
DEP <- c(0., 1.,  3, 5.,  10,  15,  30.,  60.,  100.,  200.) # Soil nodes (cm)
soil.hydro<-pedotransfer(soilpro = as.data.frame(soilpro), DEP = DEP)
PE<-soil.hydro$PE
BB<-soil.hydro$BB
BD<-soil.hydro$BD
KS<-soil.hydro$KS
BD[1:9]<-BD[1:9]#*1.7 # make top 15 cm more dense
BulkDensity <- BD[seq(1,19,2)]*1000 #soil bulk density, kg/m3
```

Get qualitative soil type out of interest.

```{r, eval=TRUE}
# search through observed textures and find the nearest match to Campell and Norman's Table 9.1
stypes<-NULL
for(m in 1:nrow(soilpro)){
 ssq<-(CampNormTbl9_1[,2]-soilpro[m,4]/100)^2 + (CampNormTbl9_1[,3]-soilpro[m,3]/100)^2
 stypes[m]<-which(ssq==min(ssq))
}

# produce a table of the qualitative soil profile
soils<-as.character(CampNormTbl9_1[,1])
profile<-as.data.frame(cbind(soilpro[,1],soils[stypes]), stringsAsFactors=FALSE)
profile[,1]<-as.numeric(profile[,1])
colnames(profile)<-c("depth","soiltype")
library(knitr)
kable(profile)
``` 

Get Leaf Area Index estimate

```{r, eval=FALSE}
monthly_LAI <- stack("W:/monthlyLAI.nc")
lonlat<-as.data.frame(longlat)
monthly_LAI <- crop(monthly_LAI, extent(lonlat[1,1]-0.1, lonlat[1,1]+0.1, lonlat[1,2]-0.1, lonlat[1,2]+0.1))
LAI_month<-extract(monthly_LAI, cbind(longlat[1],longlat[2]))
juldays12 <- c(15, 46, 74, 105, 135, 166, 196, 227, 258, 288, 319, 349)
LAI <- suppressWarnings(spline(juldays12, LAI_month, n = 365, xmin = 1, xmax = 365, method = "periodic"))$y
LAI <- rep(LAI, nyears)
```

Now run the microclimate model and get the output.

```{r, eval=FALSE}
micro<-micro_aust(loc = loc, maxshade = 70, ystart = ystart, yfinish = yfinish, PE = PE, BB = BB, BD = BD, KS = KS, BulkDensity = BulkDensity, spatial = "w:/", windfac = 1, LAI = LAI, cap = 0, TIMAXS = c(2, 1, 0, 0))
save(micro, file = "c:/Users/mrke/My Dropbox/Current Research Projects/Tiliqua rugosa/micro_SwanReach.Rda")
```

Estimate burrow humidity from weighted average vapour pressure between near-surface and soil

```{r}
load("c:/Users/mrke/My Dropbox/Current Research Projects/Tiliqua rugosa/micro_SwanReach.Rda")

sat <- WETAIR(db = micro$soil[,3:12])$esat # saturated soil vapour pressure
vpres_soil <- sat * micro$humid[,3:12] # vapour pressure in soil
e <- WETAIR(db = micro$metout[,3], rh = micro$metout[,5])$e # ambient vapour pressure (soil surface)
satmean <- vpres_soil # matrix for weighted mean vapour pressure
weights <- seq(0, .9, .1) # assume linear weighting, with ambient at surface (i.e. start at 0)
satmean <- t(apply(cbind(e, e, e, e, e, e, e, e, e, e), 1, function(x) x * (1 - weights))) + t(apply(vpres_soil, 1, function(x) x * weights)) # get weighted mean vapour pressure
newRH<-satmean / sat # compute relative humidity
newRH[newRH > 1] <- 1 # remove RH > 1
micro$humid[,3:12] <- newRH # replace values in original soil humidity matrix

# create vector of x y z values
for(i in 7:10){ # from 30 cm to 2 m
  temp <- cbind(DEP[i], satmean[,i], e)
  if(i==7){
    threeD <- temp
  }else{
    threeD <- rbind(threeD, temp)
  }
}
threeD <- as.data.frame(threeD)
colnames(threeD) <- c("depth", "soil", "ambient")

x <- threeD$depth
y <- threeD$ambient
z <- threeD$soil
x2 <- x/10
z2 <- -1403.775 + 100.521 * x2 + 3.842 * y - 7.466* x2 ^ 2 + 0.037 * x2 * y - 0.001 * y^2

spl <- scatterplot3d(threeD$depth,   # x axis
    threeD$ambient,     # y axis
    threeD$soil    # z axis
    , highlight.3d = TRUE, grid = TRUE, axis = TRUE, box = TRUE, angle = 120, scale.y = 1.5, pch = 16)

spl$points3d(x,   # x axis
    y,     # y axis
    z2,    # z axis
   pch = 16, col = 'blue')


spline <- interp(x, y, z, linear = FALSE)
spline2 <- which(spline2$x < 0)
# rotatable 3D plot of points and spline surface
open3d(scale = c(1 / diff(range(x)), 1 / diff(range(y)), 1 / diff(range(z))))
open3d(scale = c(0.0058823529, 0.0005567736, 0.0002857874))
with(spline2,surface3d(x, y, z, alpha = .2))
points3d(x, y, z2)
title3d(xlab = "", ylab = "", zlab = "")
axes3d()
```

## References

Shimmin, G. A., J. Skinner, and R. V. Baudinette. 2002. The warren architecture and environment of the southern hairy-nosed wombat (Lasiorhinus latifrons). Journal of Zoology 258:469-477.