---
title: "Tiliqua rugosa microclimate simulation at Bundey Bore"
author: "Michael Kearney"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{Tiliqua rugosa microclimate simulation at Bundey Bore}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
 eval = TRUE, tidy.opts=list(width.cutoff=60), tidy=TRUE  
)
```

## Overview

This document runs a simulation of the microclimate at Bull's Bundey Bore study site.

## Setup for the microclimate model

First load the necessary packages.

```{r}
library(NicheMapR)
library(raster)
library(dismo)
library(knitr)
```

Choose the site to simulate.

```{r}
spatial <- "w:/"
longlat<-c(139.3109, -33.888) # Bundey Bore study site
loc<-longlat
```

Specify the years to simulate

```{r}
ystart <- 1991# start year
yfinish <- 2010# end year
nyears<-yfinish-ystart+1# integer, number of years for which to run the microclimate model
```

Now set the soil properties. First retrieve soil properties from Soil and Landscape Grid of Australia (SLGA)

```{r}
prevdir<-getwd()
setwd('x:')
cmd<-paste("R --no-save --args ",longlat[1]," ",longlat[2]," < extract.R",sep='')
system(cmd)
soilpro<-read.csv('data.csv')
setwd(prevdir)
soilpro[,1]<-c(2.5,7.5,22.5,45,80,150)
colnames(soilpro)[1] <- 'depth'
```

Now get hydraulic properties for this soil using Cosby et al. 1984 pedotransfer functions.

```{r}
DEP <- c(0., 1.,  3, 5.,  10,  15,  30.,  60.,  100.,  200.) # Soil nodes (cm)
soil.hydro<-pedotransfer(soilpro = as.data.frame(soilpro), DEP = DEP)
PE<-soil.hydro$PE
BB<-soil.hydro$BB
BD<-soil.hydro$BD
KS<-soil.hydro$KS
BulkDensity <- BD[seq(1,19,2)]*1000 #soil bulk density, kg/m3
```

Get qualitative soil type out of interest.

```{r}
# search through observed textures and find the nearest match to Campell and Norman's Table 9.1
stypes<-NULL
for(m in 1:nrow(soilpro)){
  ssq<-(CampNormTbl9_1[,2]-soilpro[m,4]/100)^2 + (CampNormTbl9_1[,3]-soilpro[m,3]/100)^2
  stypes[m]<-which(ssq==min(ssq))
}

# produce a table of the qualitative soil profile
soils<-as.character(CampNormTbl9_1[,1])
profile<-as.data.frame(cbind(soilpro[,1],soils[stypes]), stringsAsFactors=FALSE)
profile[,1]<-as.numeric(profile[,1])
colnames(profile)<-c("depth","soiltype")
kable(profile)
``` 

```{r}
Usrhyt <- 0.03 # m
maxshade <- 50 # maximum simulated shade
LAI <- 0.317 # mean for the site
```

Run the model and save the output as an R data file.

```{r}
micro<-micro_aust(loc = longlat, LAI = LAI, ystart = ystart, yfinish = yfinish, PE = PE, BB = BB, BD = BD, KS = KS, BulkDensity = BulkDensity, maxshade = maxshade, Usrhyt = Usrhyt, DEP = DEP, spatial = "W:/", ERR = 2.5)
save(micro,file = 'microclimate/micro.Rda') # save output
```

Get Leaf Area Index

```
library(raster)
library(ncdf4)
setwd("c:/Spatial_Data/Soil and Vegetation/LAI")

filelist<-list.files(full.names = TRUE)[-(1:2)] # list files, remove dates and first (incomplete) file
dates<-read.csv('dates.csv', stringsAsFactors = FALSE)[,2]
dates<-dates[-1]
dates<-gsub('[.]', '-', dates)
dates<-as.POSIXct(dates,format="%Y-%m-%d")
tzone<-paste("Etc/GMT+",10,sep="") 
dates2<-seq(ISOdate(2000,02,26,tz=tzone)-3600*12, ISOdate(as.numeric(substr(dates[length(dates)],1,4)),as.numeric(substr(dates[length(dates)],6,7)),as.numeric(substr(dates[length(dates)],9,10)),tz=tzone)-3600*13, by="days") 

for(i in 1:length(filelist)){
  a<-raster(filelist[i], varname = 'lai')
  LAI<-raster::extract(a, cbind(longlat[1],longlat[2]))
  if(i==1){
    LAIs<-LAI
  }else{
    LAIs<-c(LAIs,LAI)
  }
  cat(i, '\n')
}
plot(LAIs~dates, type = 'l', main = "LAI, Bundey Bore", ylim = c(0,7))
LAIdone<-cbind(as.data.frame(dates),LAIs, stringsAsFactors=FALSE)
colnames(LAIdone)<-c("date","LAI")
setwd("C:/Users/mrke/My Dropbox/Current Research Projects/Tiliqua rugosa")
write.csv(LAIdone, 'LAI_Bundey.csv')
text(dates2[1],7,paste0("mean ",round(mean(as.numeric(LAIs), na.rm=TRUE),1)))
text(dates2[1],6.7,paste0("min ",round(min(as.numeric(LAIs), na.rm=TRUE),1)))
```

Compute monthly mean LAI.

```{r}
LAIs<-read.csv('LAI_Bundey.csv')[,3]
dates<-as.POSIXct(read.csv('LAI_Bundey.csv')[,2],format="%Y-%m-%d")
tzone<-paste("Etc/GMT+",10,sep="") 
dates2<-seq(ISOdate(2000,02,26,tz=tzone)-3600*12, ISOdate(as.numeric(substr(dates[length(dates)],1,4)),as.numeric(substr(dates[length(dates)],6,7)),as.numeric(substr(dates[length(dates)],9,10)),tz=tzone)-3600*13, by="days") 

months<-c("01","02","03","04","05","06","07","08","09","10","11","12")
LAImon<-vector(length = 12)
for(i in 1:length(months)){
LAImon[i]<-mean(subset(LAIs, format(dates, "%m") == months[i]), na.rm=TRUE)
}
plot(LAImon)
LAIfull<-rep(LAImon, nyears)
dates2=seq(ISOdate(ystart,1,1,tz=tzone)-3600*12, ISOdate((ystart+nyears),1,1,tz=tzone)-3600*13, by="days") 
dates2=subset(dates2, format(dates2, "%m/%d")!= "02/29") # remove leap yearsdates=subset(dates, 
datesmonthly<-subset(dates2, format(dates2, "%d") == "15")
LAI<-spline(x = datesmonthly, y = LAIfull, xout = dates2)$y
plot(LAI~dates2, type = 'l')
```

Run the model and save the output as an R data file.

```{r}
micro<-micro_aust(loc = longlat, LAI = LAI, ystart = ystart, yfinish = yfinish, PE = PE, BB = BB, BD = BD, KS = KS, BulkDensity = BulkDensity, maxshade = maxshade, Usrhyt = Usrhyt, DEP = DEP, scenario = scenario, year = year, spatial = "W:/")
save(micro,file = paste0('microclimate/micro_lai_',scenario,'_',year,'.Rda')) # save output
```

Get hourly rainfall

```
source('../Soil Moisture/disaggregate_rain.R')
library('RODBC')
channel <- odbcConnect("AWAPSoil")
yearlist<-seq(ystart,(ystart+(nyears-1)),1)
rainHR <- disagg_rain(loc = loc, ystart = ystart, yfinish = yfinish) 
write.table(rainHR, file="rainHR_Bundey_Bore.csv",col.names=F, row.names = F) 
```

Run the model and save the output as an R data file.

```{r}
micro<-micro_aust(loc = longlat, LAI = LAI, ystart = ystart, yfinish = yfinish, PE = PE, BB = BB, BD = BD, KS = KS, BulkDensity = BulkDensity, maxshade = maxshade, Usrhyt = Usrhyt, DEP = DEP, spatial = "W:/", rainhourly = 1, rainhour = rainHR)
save(micro,file = 'microclimate/micro_LAI_hourly.Rda.Rda') # save output
```

Soil properties for DAAS for comparison

```{r}
static_soil<-"w:/static_soil.nc"
static_soil_data<-raster::brick(static_soil)
static_soil_vars <- raster::extract(static_soil_data,cbind(loc[1],loc[2]))
labels<-c('albedo','FAPAR1','FAPAR2','FAPAR3','FAPAR4','FAPAR5','FAPAR6','FAPAR7','FAPAR8','FAPAR9','FAPAR10','FAPAR11','FAPAR12','volwater_Upper','volwater_lower','thick_upper','thick_lower','code')
colnames(static_soil_vars)<-labels

filename<-"w:/ppfInterpAll.txt"
ppf<-as.data.frame(read.table(file = filename, sep = ",", header=TRUE))
filename<-"w:/Lumped soil types.txt"
lumped.soil<-as.data.frame(read.table(file = filename, sep = ","))
filename<-"w:/SoilTypeLUT_725_AWAP.csv"
soiltype<-as.data.frame(read.table(file = filename, sep = ","))
soilcode<-subset(soiltype, soiltype[1]==static_soil_vars[1,18])
lumped<-subset(lumped.soil, V4==as.character(soilcode[1,2]))
soiltype2<-lumped[1,6]
soilprop<-subset(ppf, ppf==soilcode[1,2]) 
McKenzie2000Table2<-as.data.frame(read.csv('../Soil Moisture/McKenzie2000Table2.csv'), stringsAsFactors=FALSE)
dep1<-soilprop$Athick50
dep2<-soilprop$Bthick50
text1<-as.character(subset(McKenzie2000Table2, Texture.Group.Number==soilprop$Atext50)$Texture.Group)
text2<-as.character(subset(McKenzie2000Table2, Texture.Group.Number==soilprop$Btext50)$Texture.Group)
clay1<-soilprop$Aclay50
clay2<-soilprop$Bclay50
BD1<-soilprop$ABDensity50
BD2<-soilprop$BBDensity50

# empty arrays
PE<-rep(0,19)
BB<-PE
KS<-PE
BD<-PE

# find half-way points between given depths
DEP2<-rep(0,19)
j<-1
for(i in 1:length(DEP2-1)){ # loop through all depths
  if(i%%2==0){ # alternates between nodes to get half way points
    DEP2[i]<-DEP2[i-1]+(DEP[j]-DEP2[i-1])/2
  }else{
    DEP2[i]<-DEP[j]
    j<-j+1
  }
}
DEP2<-as.data.frame(floor(DEP2))
colnames(DEP2)<-"DEPTH"
BD[DEP2<=dep1*100]<-BD1
BD[DEP2>dep1*100]<-BD2
BB[DEP2<=dep1*100]<-subset(CampNormTbl9_1, Texture == text1)$b
BB[DEP2>dep1*100]<-subset(CampNormTbl9_1, Texture == text2)$b
KS[DEP2<=dep1*100]<-subset(CampNormTbl9_1, Texture == text1)$Ks
KS[DEP2>dep1*100]<-subset(CampNormTbl9_1, Texture == text2)$Ks
PE[DEP2<=dep1*100]<-subset(CampNormTbl9_1, Texture == text1)$airentry
PE[DEP2>dep1*100]<-subset(CampNormTbl9_1, Texture == text2)$airentry
profile<-as.data.frame(cbind(DEP, text1),stringsAsFactors=FALSE)
profile[,1]<-as.numeric(profile[,1])
colnames(profile)<-c("depth","soiltype")
profile$soiltype[DEP>dep1*100]<-text2

BulkDensity <- BD[seq(1,19,2)]*1000 #soil bulk density, kg/m3
```


Get qualitative soil type out of interest.

```{r}
# search through observed textures and find the nearest match to Campell and Norman's Table 9.1
stypes<-NULL
for(m in 1:nrow(soilpro)){
  ssq<-(CampNormTbl9_1[,2]-soilpro[m,4]/100)^2 + (CampNormTbl9_1[,3]-soilpro[m,3]/100)^2
  stypes[m]<-which(ssq==min(ssq))
}

# produce a table of the qualitative soil profile
soils<-as.character(CampNormTbl9_1[,1])
profile<-as.data.frame(cbind(soilpro[,1],soils[stypes]), stringsAsFactors=FALSE)
profile[,1]<-as.numeric(profile[,1])
colnames(profile)<-c("depth","soiltype")
kable(profile)
```  

Run the model and save the output as an R data file.

```{r}
micro<-micro_aust(loc = longlat, LAI = LAI, ystart = ystart, yfinish = yfinish, PE = PE, BB = BB, BD = BD, KS = KS, BulkDensity = BulkDensity, maxshade = maxshade, Usrhyt = Usrhyt, DEP = DEP, spatial = "W:/")
save(micro,file = 'microclimate/micro_LAI_DAAS.Rda') # save output
```

## References

Campbell, G. S., and J. M. Norman. 1998. Environmental Biophysics. Springer, New York.