---
title: "Waddleometer test: Comparison of observed and predicted (waddleometer) body activity, body temperature and body mass"
author: "Michael Kearney"
date: "`r Sys.Date()`"
output: pdf_document
classoption: landscape
vignette: >
  %\VignetteIndexEntry{Waddleometer test: Comparison of observed and predicted (waddleometer) body activity, body temperature and body mass}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
 eval = TRUE, tidy.opts = list(width.cutoff = 60), tidy = TRUE  
)
```

## Overview

This document reads in the output produced by the file "Tiliqua rugosa simulation at Bundey Bore.Rmd" and the observed $T_b$, step count and body mass and compares them for each lizard in 2009 and 2010. It saves the summary statistics (correlation coefficient, root mean square error and confusion matrix) to files in the folder 'waddle test'. 

## Set up simulation and load the input data

```{r}
# First load the necessary packages and functions

library(NicheMapR)
library(raster)
library(dismo)
library(knitr)
library(mda)
source('addTrans.R') # function for making transparent plots

# Read in ectotherm model simulation

load('ecto.Rda')

ystart <- 1991# start year
yfinish <- 2010# end year
nyears<-yfinish - ystart+1# integer, number of years for which to run the microclimate model

# extract ectotherm model output
metout <- as.data.frame(ecto$metout)
shadmet <- as.data.frame(ecto$shadmet)
soil <- as.data.frame(ecto$soil)
shadsoil <- as.data.frame(ecto$shadsoil)
rainfall <- as.data.frame(ecto$RAINFALL)
foodwaters <- as.data.frame(ecto$foodwaters)
foodlevels <- as.data.frame(ecto$foodlevels)
environ <- as.data.frame(ecto$environ)
enbal <- as.data.frame(ecto$enbal)
masbal <- as.data.frame(ecto$masbal)
humid <- as.data.frame(ecto$humid)
debout <- as.data.frame(ecto$debout)
yearout <- as.data.frame(ecto$yearout)
foodwaters <- as.data.frame(ecto$foodwaters)
foodlevels <- as.data.frame(ecto$foodlevels)
yearsout <- as.data.frame(ecto$yearsout)
environ<-cbind(environ, metout$SOLR) # add solar radiation
colnames(environ)[ncol(environ)] <- "Solar"

# append dates
tzone <- paste("Etc/GMT-",10, sep = "") # doing it this way ignores daylight savings!
dates <- seq(ISOdate(ystart, 1, 1, tz = tzone)-3600*12, ISOdate((ystart+nyears),1, 1, tz = tzone)-3600*13, by = "hours")
dates <- subset(dates, format(dates, "%m/%d")!= "02/29") # remove leap years
dates2 <- seq(ISOdate(ystart, 1, 1, tz = tzone)-3600*12, ISOdate((ystart+nyears),1, 1, tz = tzone)-3600*13, by = "days") 
dates2 <- subset(dates2, format(dates2, "%m/%d")!= "02/29") # remove leap years

debout <- as.data.frame(cbind(dates, debout))
environ <- as.data.frame(cbind(dates, environ))
masbal <- as.data.frame(cbind(dates, masbal))
enbal <- as.data.frame(cbind(dates, enbal))
soil <- as.data.frame(cbind(dates, soil))
metout <- as.data.frame(cbind(dates, metout))
shadsoil <- as.data.frame(cbind(dates, shadsoil))
shadmet <- as.data.frame(cbind(dates, shadmet))
rainfall <- as.data.frame(cbind(dates2, rainfall))
colnames(rainfall) <- c("dates", "rainfall")
```

## Ectotherm model parameters

```{r, fig.width = 18, fig.height = 13, echo = FALSE, warning = FALSE, message = FALSE, include = TRUE}
# Thermal physiology and behaviour.

TEMERGE <- 8.5 # min Tb at which they will attempt to leave retreat, from Kerr and Bull (2004)
TBASK <- 26 # min Tb at which leaves retreat, from Pamula (1997) Table 3.14
VTMIN <- 26 # minimum Tb at which activity occurs, from Pamula (1997) Table 3.42
VTMAX <- 39 # maximum Tb at which activity occurs, from Pamula (1997) Table 3.42
TPREF <- 33.5 # preferred Tb (will try and regulate to this), from Pamula (1997) Table 3.14
ctmax <- 39 # critical thermal minimum - set to same as VTmax
ctmin <- 3.5 # critical thermal maximum, from Bennet and John-Alder (1986)
mindepth <- 3 # min depth (node, 1-10) allowed
shdburrow <- 1 # use shady retreats only in hot weather

# DEB model settings.

# load the estimated DEB pars from the estimation procedure previously run in matlab.
debpars <- as.data.frame(read.csv('DEB model/DEB_pars_Tiliqua_rugosa.csv',header = FALSE))$V1 # read in DEB pars

# set core parameters
DEB <- 1
z <- debpars[8] # zoom factor (cm)
F_m <- 13290 # max spec searching rate (l/h.cm^2)
kap_X <- debpars[11] # digestion efficiency of food to reserve (-)
v <- debpars[13] / 24 # energy conductance (cm/h)
kap <- debpars[14] # kappa, fraction of mobilised reserve to growth/maintenance (-)
kap_R <- debpars[15] # reproduction efficiency (-)
p_M <- debpars[16] / 24 # specific somatic maintenance (J/cm3)
k_J <- debpars[18] / 24 # maturity maint rate coefficient (1/h)
E_G <- debpars[19] # specific cost for growth (J/cm3)
E_Hb <- debpars[20] # maturity at birth (J)
E_Hp <- debpars[21] # maturity at puberty (J)
h_a <- debpars[22] * 10 ^ -1 /(24 ^ 2) # Weibull aging acceleration (1/h^2)
s_G <- debpars[23] # Gompertz stress coefficient (-)

# set thermal respose curve paramters
T_REF <- debpars[1] - 273
TA <- debpars[2] # Arrhenius temperature (K)
TAL <- debpars[5] # low Arrhenius temperature (K)
TAH <- debpars[6] # high Arrhenius temperature (K)
TL <- debpars[3] # low temp boundary (K)
TH <- debpars[4] # hight temp boundary (K)

# set auxiliary parameters
del_M <- debpars[9] # shape coefficient (-) 
E_0 <- debpars[24] # energy of an egg (J)
mh <- 1 # survivorship of hatchling in first year
mu_E <- 585000 # molar Gibbs energy (chemical potential) of reserve (J/mol)
```

## Read in Mike Bull's data and merge with predictions

```{r}
massdata <- read.csv('waddleometer/Church_site_mass_length_noJan2010.csv')
threshold.act <- 50 # threshold steps for counting as active

#Subset to 2009-2010 and frame-shift by half an hour to account for 1/2 hr time difference in South Australia

merge <- as.data.frame(paste(with(environ, as.numeric(format(dates, "%Y"))),"_",with(environ, as.numeric(format(dates, "%m"))),"_",with(environ, as.numeric(format(dates, "%d"))),"_",environ$TIME-1, sep = ""))
colnames(merge) <- 'merge'
environ2 <- cbind(environ, merge)
environ3 <- environ2
environ4 <- subset(environ3, format(dates,"%Y")>=2009)
environ5 <- environ4
for(l in 1:nrow(environ4)){ # make values average of prev hour to account for 1/2 time diff in SA
  if(l==nrow(environ4)){
    environ5[l, 6] <- environ4[l, 6]
  }else{
    environ5[l, 6] <- environ5[l, 6]+(environ4[l+1, 6]-environ4[l, 6])/2
  }
}
```

## Loop through and plot

For each individual, 

```{r, fig.width = 18, fig.height = 13, echo = FALSE, warning = FALSE, message = FALSE, include = TRUE}
# Loop through and plot

source('getwaddle.R') # function to read in waddleometer data for particular lizard
source('aggwaddle.R') # function to aggregate waddleometer data from 2m to hourly

par(mfrow = c(2, 2)) # set up for 2 plots in 2 columns
par(oma = c(2, 2, 2, 2) + 0.1) # margin spacing stuff
par(mar = c(3, 5, 1, 1) + 0.1) # margin spacing stuff 
par(mgp = c(3, 1, 0) ) # margin spacing stuff

# start big loop to summarise all lizards, create Appendix 1 figs

yearstodo <- c(2009, 2010)
for(m in 1:2){ # loop through each year
  yeartodo <- yearstodo[m] # choose current year
  k <- 0 # counter
  curyear <- yearstodo[m]
  plotrainfall <- subset(rainfall, substr(dates, 1, 4) == yeartodo) # get rainfall
  environ_bask <- subset(environ5,  subset = (ACT >= 1 & TC >= TBASK & substr(dates, 1, 4) == yeartodo)) # get basking hrs
  environ_forage <- subset(environ5,  subset = (ACT > 1 & substr(dates, 1, 4) == yeartodo))  # get foraging hrs
  environ_night <- subset(metout,  subset = (ZEN == 90)) # get night hours
  environ_night$TIME <- environ_night$TIME / 60 - 1 # convert from mins to hrs
  doy2 <- strptime(format(plotrainfall$dates, "%y/%m/%d"), "%y/%m/%d")$yday + 1 # get simulation day of year
  plotrainfall2 <- cbind(doy2, plotrainfall) # append day of year to rainfall data
  colnames(plotrainfall2) <- c("JULDAY", "dates", "RAINFALL")
  # create body condition vector      
  desic <- subset(debout, TIME == 24 & substr(dates, 1, 4) == curyear) 
  desic <- as.data.frame(cbind(desic[,2], desic[,20]))
  colnames(desic) <- c('day', 'desic')
  
  for(i in 1:121){ # loop through all lizards

   waddledata <- get_waddle(i)
   sleepy <- waddledata$sleepy
   curyear <- waddledata$curyear
   sexlizard <- waddledata$sexlizard
   date_waddle <- waddledata$date_waddle
   sleepy_id <- waddledata$sleepy_id
   
    if(curyear==yeartodo){ # if individual's year and current year match, do the calcs
      k <- k+1 # increment counter
      doy2 <- strptime(format(plotrainfall$dates, "%y/%m/%d"), "%y/%m/%d")$yday + 1 # get simulation day of year
      plotrainfall2 <- cbind(doy2, plotrainfall) # append day of year to rainfall data
      colnames(plotrainfall2) <- c("JULDAY", "dates", "RAINFALL")
      # create body condition vector      
      desic <- subset(debout, TIME == 24 & substr(dates, 1, 4) == curyear) 
      desic <- as.data.frame(cbind(desic[,2], desic[,20]))
      colnames(desic) <- c('day', 'desic')
      
      # aggregate sleepy lizard data by hour
      sleepy <-  aggwaddle(sleepy)
      
      # create new sleepy dataset for merging
      sleepy2 <- sleepy
      sleepy2$merge <- date_waddle$Group.1
      #sleepy2$Temperature <- as.factor(sleepy$Temperature)
      
      # now merge sleepy dataset with environ dataset and 
      correl <- merge(sleepy2, environ5, by = 'merge')
      correl_day <- subset(correl, ZEN != 90) # remove nighttime hours
      correl2 <- correl[, c(2, 3, 6, 7, 8, 9, 4, 5, 15, 19, 16)]
      colnames(correl2) <- c('date','doy','year','month','day','hour','Tb_obs','steps','Tb_pred','act','shade')
      correl2.day <- correl_day[, c(2, 3, 6, 7, 8, 9, 4, 5, 15, 19, 16)]
      colnames(correl2.day) <- colnames(correl2)
      
      # get summary stats of Tb
      mean_Tb_obs <- mean(correl2$Tb_obs, na.rm = TRUE)
      max_Tb_obs <- max(correl2$Tb_obs, na.rm = TRUE)
      min_Tb_obs <- min(correl2$Tb_obs, na.rm = TRUE)
      med_Tb_obs <- median(correl2$Tb_obs, na.rm = TRUE)
      mean_Tb_pred <- mean(correl2$Tb_pred, na.rm = TRUE)
      max_Tb_pred <- max(correl2$Tb_pred, na.rm = TRUE)
      min_Tb_pred <- min(correl2$Tb_pred, na.rm = TRUE)
      med_Tb_pred <- median(correl2$Tb_pred, na.rm = TRUE)
      
      # do linear regression and correlation
      lm_Tb <- with(correl2, (lm(Tb_pred ~ Tb_obs)))
      r_Tb <- with(correl2, cor(Tb_pred, Tb_obs))
      lm_Tb_R2 <- summary(lm_Tb)$r.squared
      lm_Tb_rmsd <- sqrt(mean(((correl2$Tb_obs - correl2$Tb_pred)^2), na.rm = TRUE))
      
      # compute confusion matrix for 24hr activity predictions
      act.obs <- ifelse(correl2$steps > threshold.act, 1, 0)
      act.pred <- ifelse(correl2$act > 0, 1, 0)
      confus <- confusion(act.obs, act.pred)
      error <- attributes(confus)
      confusion <- as.data.frame(t(as.data.frame(c(confus[1:4], error$error))))
      rownames(confusion) <- NULL
      colnames(confusion) <- c('true-', 'false-', 'true+', 'false+', 'err')
      
      # compute confusion matrix for daytime activity predictions
      act.obs.day <- ifelse(correl2.day$steps > threshold.act, 1, 0)
      act.pred.day <- ifelse(correl2.day$act > 0, 1, 0)
      confus.day <- confusion(act.obs.day, act.pred.day)
      error.day <- attributes(confus.day)
      confusion.day <- as.data.frame(t(as.data.frame(c(confus.day[1:4], error.day$error))))
      rownames(confusion.day) <- NULL
      colnames(confusion.day) <- c('true-','false-','true+','false+','err')
      
      # find times when lizards were moving and not moving
      plotlizard_forage <- subset(sleepy,  subset = (Steps > threshold.act))
      plotlizard_noforage <- subset(sleepy,  subset = (Steps >= 0))
      if(k == 1){
        allforage <- cbind(plotlizard_forage, sexlizard)
        allnoforage <- plotlizard_noforage
        correl_all=correl2
      }else{
        allforage <- rbind(allforage, cbind(plotlizard_forage, sexlizard))
        allnoforage <- rbind(allnoforage, plotlizard_noforage)
        correl_all=rbind(correl_all,correl2)
      }
      
      # plot activity window, observed and predicted
      
      # limit activity window plot to time when data is available
      startdy <- 240
      finishdy <- 365
      
      # base plot, with times when data was available for a given lizard indicted 
      with(subset(plotlizard_noforage, Hours == 23), {plot(Hours+2~doy, xlim = c(startdy, finishdy),ylim = c(0, 25),xlab = "",ylab = "",cex = 1.25, pch = 15, col = 'black', cex.axis = 1.5, cex.lab = 1.5)})
      mtext(text = "hour of day",side = 2, padj = -3, cex = 1.25)
      mtext(text = "day of year",side = 1, padj = 3, cex = 1.25)
      
      # plot night hours
      with(environ_night, {points(TIME+2~JULDAY, xlim = c(startdy, finishdy), ylim = c(0, 25), xlab = "day of year", ylab = "hour of day", cex = 0.5, col = "dark grey", pch = 16)})
      
      # plot basking hours      
      with(environ_bask, {points(TIME~JULDAY, xlim = c(startdy, finishdy), ylim = c(0, 25),xlab = "day of year", ylab = "hour of day", cex = 1.,col = "light blue", pch = 15)})
      
      # plot foraging hours
      with(environ_forage, {points(TIME~JULDAY, xlim = c(startdy, finishdy), ylim = c(0, 25), xlab = "day of year", ylab = "hour of day", cex = 1., col = "gold", pch = 15)})
      
      # plot observed foraging
      with(plotlizard_forage, {points(Hours+1~doy, xlim = c(startdy, finishdy),ylim = c(0, 25),xlab = "day of year",ylab = "hour of day",cex = log(plotlizard_forage$Steps/300),pch = 15, col = addTrans("red",100))})
      
      # plot desiccation level and rainfall
      with(desic, {points(desic~day, xlim = c(startdy, finishdy),ylim = c(0, 25),xlab = "day of year",ylab = "hour of day",lwd = 2, pch = 15, col = 'grey',type = 'l',lty = 2)})
      with(plotrainfall2, {points(RAINFALL~JULDAY, type = "h",col = 'blue')})
      
      # now plot Tb trace through time
      
      # limit plot to time when data is available
      daystart <- paste(substr(curyear, 3, 4), '/08/24',sep = "") # y/m/d
      dayfin <- paste(substr(curyear, 3, 4), '/12/31',sep = "") # y/m/d
      
      # subset observed temps to observation window and ensure they are in date order
      plotlizard <- subset(sleepy, format(sleepy$date_waddle, "%y/%m/%d") >= daystart & format(sleepy$date_waddle, "%y/%m/%d") <= dayfin)
      plotlizard <- plotlizard[order(plotlizard$date_waddle),]
      
      # subset predicted lizard temps, condition and microclimate
      plotpred <- subset(environ5, format(environ5$dates, "%y/%m/%d") >= daystart & format(environ5$dates, "%y/%m/%d") <= dayfin)
      plotdeb <- subset(debout, format(debout$dates, "%y/%m/%d") >= daystart & format(environ$dates, "%y/%m/%d") <= dayfin)
      plotmetout <- subset(metout, format(metout$dates, "%y/%m/%d")>= daystart & format(metout$dates, "%y/%m/%d") <= dayfin)
      
      # merge observed and predicted to avoid continuous line between sample gaps
      plotlizard2 <- plotlizard
      colnames(plotlizard2)[1] <- "dates"
      plotlizard2 <- merge(plotlizard2, plotpred, all = TRUE)
      
      # plot predicted Tb trace
      with(plotpred, {plot(TC~dates, type = "l",ylim = c(0, 40),ylab = "",xlab = "", cex.axis = 1.5, cex.lab = 1.5)})
      mtext(text = expression(temperature~(degree*C)),side = 2, padj = -1.5, cex = 1.25)
      mtext(text = "date",side = 1, padj = 3, cex = 1.25)
      
      # plot observed Tb
      with(plotlizard2, {points(Temperature~dates, type = "l",col = addTrans("red",150))})
      
      # plot predicted desiccation level and rainfall
      with(plotdeb, {points(Body_cond~dates, type = "l",col = 'grey',lty = 2, lwd = 2)})
      with(plotrainfall2, {points(RAINFALL~dates, type = "h",col = 'blue')})
      
      # plot predicted body mass, excluding reproductive mass and subtracting away any mass lost as evaporation
      
      hydration_mass_female <- with(plotdeb,WETMASS - WETMASS * (Body_cond / 100))
      hydration_mass_male <- with(plotdeb,WETMASS - (CUMREPRO+CUMBATCH) / mu_E*23.9 / 0.3 - WETMASS * (Body_cond / 100))
      
      if(sexlizard != "M"){
        hydration_mass <- hydration_mass_female
      }else{
        hydration_mass <- hydration_mass_male
      }
      with(plotdeb,{plot(hydration_mass ~ dates, type = 'l', ylim = c(400, 1100),ylab = "", xlab = "", cex.axis = 1.5, cex.lab = 1.5)})
      mtext(text = "mass, g",side = 2, padj = -3, cex = 1.25)
      mtext(text = "date",side = 1, padj = 3, cex = 1.25)
      
      # plot observed mass
      massobs <- subset(massdata, lizard_ID==sleepy_id)
      date_mass <- as.POSIXct(with(massobs, ISOdatetime(year, month, day, 0, 0, 0)))
      doymass <- strptime(format(date_mass, "%y/%m/%d"), "%y/%m/%d")$yday + 1
      massobs <- cbind(massobs, date_mass, doymass)
      with(massobs,{points(wgt~date_mass, type = 'p',col = 'red')})
 hydration_mass_female <- with(plotdeb,WETMASS - WETMASS * (Body_cond / 100))
      hydration_mass_male <- with(plotdeb,WETMASS - (CUMREPRO+CUMBATCH) / mu_E*23.9 / 0.3 - WETMASS * (Body_cond / 100))
      
      if(sexlizard != "M"){
        hydration_mass <- hydration_mass_female
      }else{
        hydration_mass <- hydration_mass_male
      }                  
      dailymass_female <- aggregate(hydration_mass_female, by = list(format(plotdeb$dates, "%Y-%m-%d")), FUN = mean)
      dailymass_male <- aggregate(hydration_mass_male, by = list(format(plotdeb$dates, "%Y-%m-%d")), FUN = mean) 
      if(sexlizard == "M"){
        dailymass <- dailymass_male
      }else{
        dailymass <- dailymass_female
      }
      
      massobs2 <- massobs[order(as.Date(massobs$date.1, "%d/%m/%Y")),]
      massobs2 <- massobs2[grep(as.character(curyear), massobs2$date.1),]
      massobs2 <- cbind(massobs2, dailymass[which(dailymass$Group.1 %in% as.character(as.Date(as.character(massobs2$date.1), "%d/%m/%Y"))),2])
      colnames(massobs2)[22] <- "PredMass"
      
      # plot
      #x <- c(400:1000)
      #plot(x,x, type = 'l', main='body condition',ylab = "observed mass, g", xlab = "predicted mass, g", ylim = c(400, 1000), cex.axis = 1.2, cex.lab = 1.2)
      #points(massobs2$wgt ~ massobs2$PredMass, col = "black", pch = 16, cex = 1.5)
      
      # compute correlation coefficient and root mean square deviation
      mass.r <- cor(massobs2$wgt[is.na(massobs2$wgt)==FALSE], massobs2$PredMass[is.na(massobs2$wgt)==FALSE])
      mass.rmsd <- sqrt(mean(((massobs2$wgt-massobs2$PredMass) ^ 2),na.rm = TRUE))
      mass.n <- nrow(massobs2)
      # append to plot
      #text(plotdeb$dates[1] + 3600*24*15,1000, "         r     rmsd", cex = 1.75)
      #text(plotdeb$dates[1] + 3600*24*10,930, paste0('model fit ',round(mass.r),'   ',round(mass.rmsd, 2)))
      text(plotdeb$dates[1] + 3600*24*10,970, paste("r = ",round(mass.r, 2),"\n","rmsd = ",round(mass.rmsd, 2),sep = ""), cex = 1.75)      
      
      # plot predicted vs. observed body temperature
      with(correl2,(plot(Tb_pred~Tb_obs, ylim = c(0, 40),xlim = c(0, 40), xlab = "", ylab = "", cex.axis = 1.5, cex.lab = 1.5)))
      mtext(text = expression('predicted T'[b]),side = 2, padj = -3, cex = 1.25)
      mtext(text = expression('observed T'[b]),side = 1, padj = 3, cex = 1.25)
      abline(0, 1)
      text(5, 35, paste("r = ",round(r_Tb, 2),"\n","rmsd = ",round(lm_Tb_rmsd, 2),sep = ""), cex = 1.75)
      title(main = paste(sleepy_id," sex =",sexlizard," ",curyear, sep = " "),outer = T, cex.main = 2)
      cat('\r\n\r\n')      

      # construct summary table
      if(k==1){
        summary <- as.data.frame(cbind(as.numeric(sleepy_id),sexlizard, curyear, mean_Tb_obs, mean_Tb_pred, max_Tb_obs, max_Tb_pred, min_Tb_obs, min_Tb_pred, med_Tb_obs, med_Tb_pred, r_Tb, lm_Tb_rmsd, confusion, confusion.day, mass.r, mass.rmsd, mass.n))
      }else{
        summary <- rbind(summary, as.data.frame(cbind(as.numeric(sleepy_id),sexlizard, curyear, mean_Tb_obs, mean_Tb_pred, max_Tb_obs, max_Tb_pred, min_Tb_obs, min_Tb_pred, med_Tb_obs, med_Tb_pred, r_Tb, lm_Tb_rmsd, confusion, confusion.day, mass.r, mass.rmsd, mass.n)))
      } 
    }
  } #end loop through lizards
  
  colnames(summary) <- c('id','sex','year','mean_Tb_obs','mean_Tb_pred','max_Tb_obs','max_Tb_pred','min_Tb_obs','min_Tb_pred','med_Tb_obs','med_Tb_pred','Tb_r','Tb_rmsd','true-','false-','true+','false+','err','day.true-','day.false-','day.true+','day.false+','day.err', 'mass_R', 'mass_rmsd', 'mass_n')
  
  # write out summary table
  if(yeartodo==2009){
    write.csv(summary,'summary_nodrink_2009.csv')
    write.csv(correl_all,'correl_all_2009.csv')
    write.csv(allforage, 'allforage_2009.csv')
    write.csv(allnoforage, 'allnoforage_2009.csv')
  }else{
    correl_all_2010=correl_all
    write.csv(summary,'summary_nodrink_2010.csv')
    write.csv(correl_all,'correl_all_2010.csv')
    write.csv(allforage, 'allforage_2010.csv')
    write.csv(allnoforage, 'allnoforage_2010.csv')    
  }   
}
```